---
title: "Bayesian Modeling with LLM Priors"
author: "Aaron Gardony agardony@gmail.com"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8, dpi = 300)
```

# Introduction

This notebook performs Bayesian analysis on MaxDiff survey results using informative priors derived from LLM data. The objective is to assess if including priors from the LLM data allows for similar results as modeling the entire human dataset.

# Libraries

```{r libraries}
library(tidyverse)
library(readxl)
library(brms)
library(cmdstanr)
library(emmeans)
library(tidybayes)
library(janitor)
library(tictoc)
library(psych)
```

```{r simulation_parameters}
n_simulations <- 100
n_users <- 30
```


# Data Loading

```{r load_data}
# Load LLM data
llm_responses <- read_csv("../maxdiff_data/temp_2OpenAI_2Google_1Anthropic/maxdiff_responses.csv") |> 
  clean_names()  # Clean column names

# Load human data
human_data_indiv_choices <- read_excel("../maxdiff_data/QUX Survey_ Spring '24 - MaxDiff_Future Programming Design & choices (1).xlsx") |> 
  clean_names()  # Clean column names
human_data_indiv_choices <- human_data_indiv_choices |> mutate(across(everything(), factor))
human_data_indiv_choices$item <- as.factor(unname(human_data_indiv_choices$item))

# Create a mapping of long names to short names
class_names<- c(
  "Choice Modeling Hands-On: Introduction to Conjoint Analysis and MaxDiff",
  "Survey Masterclass: Intensive Review of Best Practices for Online Surveys", 
  "Log Sequence Analysis: Tools to Visualize, Model, and Understand Instrument Logs",
  "Psychometrics for Survey Scales: Reliability and Validity Assessment for Practitioners",
  "R-Intensive: In-Person R Programming Bootcamp for Social Scientists in Industry",
  "The Price is Right: Best Practices in Pricing Research",
  "HEART UX Metrics Deep Dive: From Best Practices to Leading HEART Workshops with Your Team",
  "Introduction to Bayesian Statistics: Linear and Hierarchical Linear Bayesian Models in R",
  "Text Analytics 0 to 60: Sentiment Analysis and Topic Modeling with Natural Language Texts",
  "Yes, It is Causation, and not Correlation: Models for Causal Inference in R",
  "Interviewer Training: Improving Your Team's Quant UX Interview Process",
  "Advanced Choice Modeling Surveys: Advanced Options Beyond Standard Conjoint and MaxDiff",
  "Segmentation: Running a Successful Segmentation Effort, from the Models through Team Politics",
  "UX Metrics Sprintmaster Training: How to Lead UX Metrics Sprints"
)

# Create a mapping of long names to short names
name_mapping <- c(
  "Choice Modeling Hands-On: Introduction to Conjoint Analysis and MaxDiff" = "Choice Models",
  "Survey Masterclass: Intensive Review of Best Practices for Online Surveys" = "Surveys", 
  "Log Sequence Analysis: Tools to Visualize, Model, and Understand Instrument Logs" = "Log Sequences",
  "Psychometrics for Survey Scales: Reliability and Validity Assessment for Practitioners" = "Psychometrics",
  "R-Intensive: In-Person R Programming Bootcamp for Social Scientists in Industry" = "R Programming",
  "The Price is Right: Best Practices in Pricing Research" = "Pricing",
  "HEART UX Metrics Deep Dive: From Best Practices to Leading HEART Workshops with Your Team" = "UX Metrics",
  "Introduction to Bayesian Statistics: Linear and Hierarchical Linear Bayesian Models in R" = "Bayes Stats",
  "Text Analytics 0 to 60: Sentiment Analysis and Topic Modeling with Natural Language Texts" = "Text Analytics",
  "Yes, It is Causation, and not Correlation: Models for Causal Inference in R" = "Causal Models",
  "Interviewer Training: Improving Your Team's Quant UX Interview Process" = "Interviewer-ing",
  "Advanced Choice Modeling Surveys: Advanced Options Beyond Standard Conjoint and MaxDiff" = "Advanced Choice",
  "Segmentation: Running a Successful Segmentation Effort, from the Models through Team Politics" = "Segmentation",
  "UX Metrics Sprintmaster Training: How to Lead UX Metrics Sprints" = "Metrics Sprints"
)

# Calculate individual-level utility scores using tidyverse
llm_responses <- llm_responses |>
  mutate(
    user_id = str_c(model_name, persona_index, sep = "_"),
    model_clean = case_when(
      str_detect(tolower(model_name), "gpt") ~ "GPT",
      str_detect(tolower(model_name), "claude") ~ "Claude", 
      str_detect(tolower(model_name), "gemini") ~ "Gemini",
      TRUE ~ model_name
    )
  )

# convert numeric responses to strings for compatibility with brms
human_data_indiv_choices <- human_data_indiv_choices |>
  mutate(
    response = case_when(
      response == 1 ~ "best",
      response == -1 ~ "worst", 
      response == 0 ~ "neither"
    )
  )
```


# Convert LLM responses to long format

```{r convert_llm_responses_to_long}
library(tidyr)

# Create item lookup table from class_names
item_lookup <- tibble(
  item_name = as.character(class_names),
  item = 1:length(class_names)
)

# Function to format LLM responses to match human_data_indiv_choices structure
format_llm_to_individual_choices <- function(data) {
  
  formatted_data <- data |>
    mutate(original_row_id = row_number()) |>
    # Use pattern matching to find which class_names appear in each trial_items string
    rowwise() |>
    mutate(
      matched_items = list({
        matches <- character(0)
        for(class_name in as.character(class_names)) {
          if(str_detect(trial_items, fixed(class_name))) {
            matches <- c(matches, class_name)
          }
        }
        matches
      })
    ) |>
    ungroup() |>
    # Unnest to create separate rows for each matched item
    unnest(matched_items) |>
    # Join with item lookup table to get numeric item IDs
    left_join(item_lookup, by = c("matched_items" = "item_name")) |>
    # Strip names from item column to get just numeric values
    mutate(item = as.numeric(item)) |>
    # Create position within each original trial (1-5 for each original row)
    group_by(original_row_id) |>
    mutate(position = row_number()) |>
    ungroup() |>
    # Create response column based on best/worst item selections
    mutate(
      response = case_when(
        matched_items == best_item_name ~ 1,   # best choice gets 1
        matched_items == worst_item_name ~ -1, # worst choice gets -1
        TRUE ~ 0                               # not selected items get 0
      )
    ) |>
    # Select and rename columns to match human_data_indiv_choices format
    select(
      record_id = user_id,
      task = trial_number,
      position,
      item,
      response
    ) |>
    filter(!is.na(item)) |>
    arrange(record_id, task, position)
  
  return(formatted_data)
}

# Apply the transformation
llm_responses_formatted <- format_llm_to_individual_choices(llm_responses)
```

# Bayesian Modeling with LLM Data

```{r bayesian_llm_modeling}
library(afex)
afex::set_sum_contrasts()

# Prepare LLM data

# convert numeric responses to strings for compatibility with brms
llm_responses_formatted <- llm_responses_formatted |>
  mutate(
    response = case_when(
      response == 1 ~ "best",
      response == -1 ~ "worst", 
      response == 0 ~ "neither"
    )
  )

# factor conversion
llm_responses_formatted <- llm_responses_formatted |> mutate(across(everything(), factor))
llm_responses_formatted$item <- as.factor(unname(llm_responses_formatted$item)) # strip the names

# Construct the Bayesian model for LLM
model_llm <- brm(
  bf(response ~ 0 + item + (1 | ID | record_id)),
  data = llm_responses_formatted,
  family = categorical(refcat = "worst"),
  prior = c(
    prior(normal(0, 3), class = b, dpar = mubest),
    prior(normal(0, 3), class = b, dpar = muneither),
    prior(exponential(1), class = sd, dpar = mubest),
    prior(exponential(1), class = sd, dpar = muneither)
  ),
  chains = 4, cores = 4, iter = 2000, seed = 1234,
  backend = "cmdstanr", threads = threading(2),
  file = "model_llm",
  silent = FALSE
)
```


# Generate Priors from LLM Model
```{r generate_priors}
# Extract posterior draws for mubest coefficients
llm_mubest_draws <- model_llm |> 
  gather_draws(`^b_mubest_item.*$`, regex = TRUE)

# Extract posterior draws for muneither coefficients
llm_muneither_draws <- model_llm |> 
  gather_draws(`^b_muneither_item.*$`, regex = TRUE)

# Calculate mean and HDI for mubest coefficients
llm_mubest_priors_df <- llm_mubest_draws |>
  group_by(.variable) |>
  summarise(
    mean_est = mean(.value),
    mean_sd = sd(.value),
    #hdi_lower = hdi(.value)[1],
    #hdi_upper = hdi(.value)[2],
    #hdi_width = hdi_upper - hdi_lower,
    .groups = "drop"
  ) |>
  mutate(
    # Construct weakly informative prior mean and sd
    prior_mean = mean_est,
    prior_sd = mean_sd * 10#hdi_width * 2
  )

# Calculate mean and HDI for muneither coefficients
llm_muneither_priors_df <- llm_muneither_draws |>
  group_by(.variable) |>
  summarise(
    mean_est = mean(.value),
    mean_sd = sd(.value),
    #hdi_lower = hdi(.value)[1],
    #hdi_upper = hdi(.value)[2],
    #hdi_width = hdi_upper - hdi_lower,
    .groups = "drop"
  ) |>
  mutate(
    # Construct weakly informative prior mean and sd
    prior_mean = mean_est,
    prior_sd = mean_sd * 10#hdi_width
  )

# Create prior specifications for brms
priors <- NULL

# Add mubest priors
for(i in 1:nrow(llm_mubest_priors_df)) {
  coef_name <- str_remove(llm_mubest_priors_df$.variable[i], "b_mubest_")
  
  new_prior <- prior_string(paste0("normal(", llm_mubest_priors_df$prior_mean[i], ", ", llm_mubest_priors_df$prior_sd[i], ")"), 
                           class = "b", 
                           coef = coef_name,
                           dpar = "mubest")
  
  priors <- if(is.null(priors)) new_prior else priors + new_prior
}

# Add muneither priors
for(i in 1:nrow(llm_muneither_priors_df)) {
  coef_name <- str_remove(llm_muneither_priors_df$.variable[i], "b_muneither_")
  
  new_prior <- prior_string(paste0("normal(", llm_muneither_priors_df$prior_mean[i], ", ", llm_muneither_priors_df$prior_sd[i], ")"), 
                           class = "b", 
                           coef = coef_name,
                           dpar = "muneither")
  
  priors <- priors + new_prior
}

# Add priors for sd parameters
priors <- c(priors,
  prior(exponential(1), class = sd, dpar = mubest),
  prior(exponential(1), class = sd, dpar = muneither)
)
```

# Fit Omnibus Model with All Human Data (Run Once)

```{r omnibus_model}
# Fit the omnibus model with all human data
model_human_omnibus <- brm(
  bf(response ~ 0 + item + (1 | ID | record_id)),
  data = human_data_indiv_choices,
  family = categorical(refcat = "worst"),
  prior = c(
    prior(normal(0, 3), class = b, dpar = mubest),
    prior(normal(0, 3), class = b, dpar = muneither),
    prior(exponential(1), class = sd, dpar = mubest),
    prior(exponential(1), class = sd, dpar = muneither)
  ),
  chains = 4, cores = 4, iter = 2000, seed = 1234,
  backend = "cmdstanr", threads = threading(2),
  file = "model_human_omnibus",
  silent = FALSE
)

# Get omnibus model mubest coefficients (these remain constant across n_users loops)
omnibus_mubest <- fixef(model_human_omnibus)[grepl("mubest", rownames(fixef(model_human_omnibus))), "Estimate"]
names(omnibus_mubest) <- str_remove(names(omnibus_mubest), "mubest_")

# Get omnibus model mubest standard deviations
omnibus_mubest_sds <- fixef(model_human_omnibus)[grepl("mubest", rownames(fixef(model_human_omnibus))), "Est.Error"]
names(omnibus_mubest_sds) <- str_remove(names(omnibus_mubest_sds), "mubest_")

# Calculate mean SD for omnibus model
mean_sd_omnibus <- mean(omnibus_mubest_sds)

# Calculate LLM prior ranking correlation (constant across n_users loops)
prior_betas <- llm_mubest_priors_df |> arrange(nchar(.variable), .variable) |> select(.variable, mean_est)
prior_ranks <- rank(-prior_betas$mean_est)
names(prior_ranks) = names(omnibus_mubest)
omnibus_ranks <- rank(-omnibus_mubest)
cor_prior_ranks <- cor(omnibus_ranks, prior_ranks, method = "spearman")
```

# Bayesian Modeling on Random Human Samples

```{r bayesian_human_sample_modeling}
set.seed(1234)
# Create random samples from the human data
user_ids <- unique(human_data_indiv_choices$record_id)
results_list_llm_prior <- list()
results_list_flat_prior <- list()
# Add lists to store standard deviations
results_sds_llm_prior <- list()
results_sds_flat_prior <- list()

tic.clearlog()
for (i in 1:n_simulations) {
  tic()
  # Sample {n_users} users
  random_user_ids <- sample(user_ids, n_users)
  sampled_data <- human_data_indiv_choices %>%
    filter(record_id %in% random_user_ids)
  
  # Fit model with informative priors from LLM
  llm_informed_prior_model <- brm(
    formula = response ~ 0 + item + (1 | ID | record_id),
    data = sampled_data,
    family = categorical(refcat = "worst"),
    prior = priors,
    chains = 4, cores = 4, iter = 1000, seed = 1234,
    backend = "cmdstanr", threads = threading(2),
    refresh = 0,
    silent = 2
  )
  flat_prior_model <- brm(
    formula = response ~ 0 + item + (1 | ID | record_id),
    data = sampled_data,
    family = categorical(refcat = "worst"),
    #prior = priors,
    chains = 4, cores = 4, iter = 1000, seed = 1234,
    backend = "cmdstanr", threads = threading(2),
    refresh = 0,
    silent = 2
  )
  
  # Extract mubest coefficients directly from the models
  mubest_coefs_llm_prior <- fixef(llm_informed_prior_model)[grepl("mubest", x = rownames(fixef(llm_informed_prior_model))), "Estimate"]
  results_list_llm_prior[[i]] <- mubest_coefs_llm_prior
  
  mubest_coefs_flat_prior <- fixef(flat_prior_model)[grepl("mubest", rownames(fixef(flat_prior_model))), "Estimate"]
  results_list_flat_prior[[i]] <- mubest_coefs_flat_prior
  
  # Extract mubest standard deviations from the models
  mubest_sds_llm_prior <- fixef(llm_informed_prior_model)[grepl("mubest", x = rownames(fixef(llm_informed_prior_model))), "Est.Error"]
  results_sds_llm_prior[[i]] <- mubest_sds_llm_prior
  
  mubest_sds_flat_prior <- fixef(flat_prior_model)[grepl("mubest", rownames(fixef(flat_prior_model))), "Est.Error"]
  results_sds_flat_prior[[i]] <- mubest_sds_flat_prior
  
  toc(log = TRUE, quiet = TRUE)
  
  # Progress indicator
  if (i %% 5 == 0) {
  cat("Completed", i, "of", n_simulations, "simulations\n")
  
  # Get all timing data
  timing_log <- tic.log(format = FALSE)
  
  if (length(timing_log) > 0) {
    # Calculate total elapsed time for all iterations so far
    total_elapsed <- sum(sapply(timing_log, function(x) x$toc - x$tic))
    
    # Average time per iteration
    avg_time_per_iteration <- total_elapsed / i
    
    # Estimate remaining time
    remaining_time_minutes <- (n_simulations - i) * avg_time_per_iteration / 60
    
    cat("Avg per iteration:", round(avg_time_per_iteration, 1), "sec |", 
        "ETA:", round(remaining_time_minutes, 1), "min\n\n")
  }
}
}
```

# Analysis of Results

```{r analyze_results}
# Calculate Spearman correlations and top 5 item overlap for LLM prior
sample_correlations_llm_prior <- sapply(results_list_llm_prior, function(sample_mubest) {
  # Ensure same ordering of items
  names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
  
  # Create rankings
  omnibus_ranks <- rank(-omnibus_mubest)
  sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
  
  # Calculate Spearman correlation
  cor(omnibus_ranks, sample_ranks, method = "spearman")
})

# Calculate mean SDs for LLM prior samples
sample_sds_llm_prior <- sapply(results_sds_llm_prior, function(sample_sds) {
  return(mean(sample_sds))
})

# Calculate mean SD across all LLM prior samples
mean_sd_llm_prior <- mean(sample_sds_llm_prior)

top5_overlap_llm_prior <- sapply(results_list_llm_prior, function(sample_mubest) {
  # Ensure same ordering of items
  names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
  
  # Create rankings
  omnibus_ranks <- rank(-omnibus_mubest)
  sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
  
  # Get top 5 items for each ranking (highest ranks)
  omnibus_top5 <- names(sort(omnibus_ranks, decreasing = TRUE)[1:5])
  sample_top5 <- names(sort(sample_ranks, decreasing = TRUE)[1:5])
  
  # Calculate proportion of overlap
  overlap_count <- length(intersect(omnibus_top5, sample_top5))
  overlap_proportion <- overlap_count / 5
  
  return(overlap_proportion)
})

# Calculate Spearman correlations and top 5 item overlap for flat prior
sample_correlations_flat_prior <- sapply(results_list_flat_prior, function(sample_mubest) {
  # Ensure same ordering of items
  names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
  
  # Create rankings
  omnibus_ranks <- rank(-omnibus_mubest)
  sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
  
  # Calculate Spearman correlation
  cor(omnibus_ranks, sample_ranks, method = "spearman")
})

# Calculate mean SDs for flat prior samples
sample_sds_flat_prior <- sapply(results_sds_flat_prior, function(sample_sds) {
  return(mean(sample_sds))
})

# Calculate mean SD across all flat prior samples
mean_sd_flat_prior <- mean(sample_sds_flat_prior)

top5_overlap_flat_prior <- sapply(results_list_flat_prior, function(sample_mubest) {
  # Ensure same ordering of items
  names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
  
  # Create rankings
  omnibus_ranks <- rank(-omnibus_mubest)
  sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
  
  # Get top 5 items for each ranking (highest ranks)
  omnibus_top5 <- names(sort(omnibus_ranks, decreasing = TRUE)[1:5])
  sample_top5 <- names(sort(sample_ranks, decreasing = TRUE)[1:5])
  
  # Calculate proportion of overlap
  overlap_count <- length(intersect(omnibus_top5, sample_top5))
  overlap_proportion <- overlap_count / 5
  
  return(overlap_proportion)
})

# Calculate mean top 5 overlap proportions
mean_top5_overlap_llm <- mean(top5_overlap_llm_prior)
mean_top5_overlap_flat <- mean(top5_overlap_flat_prior)

# Calculate probability that top human item is in top 5 LLM sets
top_human_in_llm_top5 <- sapply(results_list_llm_prior, function(sample_mubest) {
  names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
  omnibus_ranks <- rank(-omnibus_mubest)
  sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
  top_human_item <- names(which(omnibus_ranks == max(omnibus_ranks)))
  sample_top5 <- names(sort(sample_ranks, decreasing = TRUE)[1:5])
  as.numeric(top_human_item %in% sample_top5)
})

top_human_in_flat_top5 <- sapply(results_list_flat_prior, function(sample_mubest) {
  names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
  omnibus_ranks <- rank(-omnibus_mubest)
  sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
  top_human_item <- names(which(omnibus_ranks == max(omnibus_ranks)))
  sample_top5 <- names(sort(sample_ranks, decreasing = TRUE)[1:5])
  as.numeric(top_human_item %in% sample_top5)
})

# Calculate probabilities
prob_top_human_in_llm_top5 <- mean(top_human_in_llm_top5)
prob_top_human_in_flat_top5 <- mean(top_human_in_flat_top5)

# Calculate probability of exact top item match
top_item_matches_llm_prior <- sapply(results_list_llm_prior, function(sample_mubest) {
  names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
  omnibus_ranks <- rank(-omnibus_mubest)
  sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
  omnibus_top <- names(which(omnibus_ranks == max(omnibus_ranks)))
  sample_top <- names(which(sample_ranks == max(sample_ranks)))
  as.numeric(omnibus_top == sample_top)
})

top_item_matches_flat_prior <- sapply(results_list_flat_prior, function(sample_mubest) {
  names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
  omnibus_ranks <- rank(-omnibus_mubest)
  sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
  omnibus_top <- names(which(omnibus_ranks == max(omnibus_ranks)))
  sample_top <- names(which(sample_ranks == max(sample_ranks)))
  as.numeric(omnibus_top == sample_top)
})

prob_correct_llm <- mean(top_item_matches_llm_prior)
prob_correct_flat <- mean(top_item_matches_flat_prior)

## Visualize Distributions of Correlations (Side-by-side)

# Create combined data frame for both prior types
correlation_df <- tibble(
  rho = c(sample_correlations_llm_prior, sample_correlations_flat_prior),
  prior_type = rep(c("LLM Prior", "Flat Prior"), 
                   c(length(sample_correlations_llm_prior), 
                     length(sample_correlations_flat_prior)))
)

# Create side-by-side density plots
correlation_plot <- ggplot(correlation_df, aes(x = rho)) +
  geom_density(aes(fill = prior_type), alpha = 0.3) +
  scale_fill_manual(name = "Prior Type",
                    labels = c("Flat Prior", "LLM-Informed Prior"), 
                    values = c("#E69F00", "#0072B2")) + 
  scale_color_manual(name = "Prior Type",
                    labels = c("Flat Prior", "LLM-Informed Prior"), 
                    values = c("#E69F00", "#0072B2")) + 
  geom_vline(data = correlation_df %>% 
               group_by(prior_type) %>% 
               summarise(median_rho = median(rho)), 
             aes(xintercept = median_rho, color = prior_type), 
             linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = cor_prior_ranks), color = "red", alpha = 0.2, 
             linetype = "solid", size = 1) +
  # Add horizontal labels for dashed lines
  geom_text(data = correlation_df %>% 
              group_by(prior_type) %>% 
              summarise(median_rho = median(rho)) %>%
              mutate(
                label = paste0("ρ=", sprintf("%.2f", median_rho)),
                hjust_val = ifelse(prior_type == "Flat Prior", 1.1, -0.1),  # Left of line for flat, right for LLM
                text_color = ifelse(prior_type == "Flat Prior", "#E69F00", "#0072B2")
              ),
            aes(x = median_rho, y = 14, label = label, hjust = hjust_val),
            color = correlation_df %>% 
              group_by(prior_type) %>% 
              summarise(median_rho = median(rho)) %>%
              mutate(text_color = ifelse(prior_type == "Flat Prior", "#E69F00", "#0072B2")) %>%
              pull(text_color),
            size = 4, fontface = "bold",
            inherit.aes = FALSE) +
  # Add text overlay
  geom_label(data = data.frame(x = 0.02, y = 11.2), 
             aes(x = x, y = y), 
             label = paste0("Mean SD of Estimates (Uncertainty):\nOmnibus = ",
                           round(mean_sd_omnibus, 3),
                           "\nLLM Prior = ",
                           round(mean_sd_llm_prior, 2),
                           "\nFlat Prior = ",
                           round(mean_sd_flat_prior, 2),
                           "\n\nMean % overlap (top 5 items):\nLLM Prior = ", 
                           round(mean_top5_overlap_llm, 2), 
                           "\nFlat Prior = ", 
                           round(mean_top5_overlap_flat, 2),
                           "\n\nMean P(top item in top 5):\nLLM Prior = ",
                           round(prob_top_human_in_llm_top5, 2),
                           "\nFlat Prior = ",
                           round(prob_top_human_in_flat_top5, 2),
                           "\n\nP(exact top item match):\nLLM Prior = ",
                           round(prob_correct_llm, 2),
                           "\nFlat Prior = ",
                           round(prob_correct_flat, 2)),
             hjust = 0, vjust = 1, size = 3.5, 
             color = "black", fontface = "bold",fill = "white", 
             label.padding = unit(0.3, "lines"),
             inherit.aes = FALSE) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 15), breaks = seq(0, 15, 5)) +
  labs(
    x = "Spearman Correlation (ρ)",
    y = "Density",
    title = "Distributions of Sub-Sample Ranking Alignment with Full Sample by Prior Type",
    subtitle = paste0("n=", n_users, " human samples and full human dataset (n=308)"),
    caption = "Red line: LLM-based prior rank correlation with full sample. Dashed line: Correlation distribution medians for each model."
  ) +
  theme_minimal() +
  theme(
  plot.title = element_text(size = 20, face = "bold"),
  plot.subtitle = element_text(size = 16),
  strip.text = element_text(size = 16, face = "bold"),
  legend.position = "bottom",
  legend.text = element_text(size = 16),
  legend.title = element_text(size = 16),
  axis.title = element_text(size = 14),
  axis.text = element_text(size = 14),
  plot.caption = element_text(size = 12, color = "gray50", hjust = 0),
)

print(correlation_plot)

  # Save the plot
  ggsave(filename = paste0("correlation_plot_", n_users, ".png"), 
         plot = correlation_plot, width = 12, height = 9, dpi = 300, bg = "white")

# Statistical tests
fisherZTest <- psych::r.test(n = n_simulations, r12 = mean(sample_correlations_llm_prior), r34 = mean(sample_correlations_flat_prior))
fisherZTest_llm_0.7 <- psych::r.test(n = length(omnibus_mubest), r12 = mean(sample_correlations_llm_prior), r34 = 0.7)
fisherZTest_flat_0.7 <- psych::r.test(n = length(omnibus_mubest), r12 = mean(sample_correlations_flat_prior), r34 = 0.7)

# t-test for top 5 overlap
top5_ttest <- t.test(top5_overlap_llm_prior, top5_overlap_flat_prior)

# Proportion tests
top_human_prop_test <- prop.test(c(sum(top_human_in_llm_top5), sum(top_human_in_flat_top5)),
                                 c(length(top_human_in_llm_top5), length(top_human_in_flat_top5)))

exact_top_prop_test <- prop.test(c(sum(top_item_matches_llm_prior), sum(top_item_matches_flat_prior)),
                                 c(length(top_item_matches_llm_prior), length(top_item_matches_flat_prior)))
```

# Summary of Results
```{r print_summary}
# Summary statistics for both prior types
cat("\n=== SUMMARY FOR n_users = ", n_users, " ===\n")
cat("LLM Prior - Mean correlation:", round(mean(sample_correlations_llm_prior), 3), "\n")
cat("Flat Prior - Mean correlation:", round(mean(sample_correlations_flat_prior), 3), "\n")
cat("Difference (LLM - Flat):", round(mean(sample_correlations_llm_prior) - mean(sample_correlations_flat_prior), 3), "\n")
cat("Fisher Z test p-value:", round(fisherZTest$p, 4), "\n")
cat("Mean top 5 overlap - LLM:", round(mean_top5_overlap_llm, 3), "| Flat:", round(mean_top5_overlap_flat, 3), "\n")
cat("P(exact top match) - LLM:", round(prob_correct_llm, 3), "| Flat:", round(prob_correct_flat, 3), "\n\n")
```

