---
title: "Bayesian Modeling with LLM Priors"
author: "Aaron Gardony agardony@gmail.com"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8, dpi = 300)
```

# Introduction

This notebook performs Bayesian analysis on MaxDiff survey results using informative priors derived from LLM data. The objective is to assess if including priors from the LLM data allows for similar results as modeling the entire human dataset.

# Libraries

```{r libraries}
library(tidyverse)
library(readxl)
library(brms)
library(cmdstanr)
library(emmeans)
library(tidybayes)
library(janitor)
library(tictoc)
library(psych)
```

```{r simulation_parameters}
n_simulations <- 100
n_users <- c(3,15,30,60,90)
```

# Data Loading

```{r load_data}
# Load LLM data
llm_responses <- read_csv("../maxdiff_data/temp_2OpenAI_2Google_1Anthropic/maxdiff_responses.csv") |> 
  clean_names()  # Clean column names

# Load human data
human_data_indiv_choices <- read_excel("../maxdiff_data/QUX Survey_ Spring '24 - MaxDiff_Future Programming Design & choices (1).xlsx") |> 
  clean_names()  # Clean column names
human_data_indiv_choices <- human_data_indiv_choices |> mutate(across(everything(), factor))
human_data_indiv_choices$item <- as.factor(unname(human_data_indiv_choices$item))

# Create a mapping of long names to short names
class_names<- c(
  "Choice Modeling Hands-On: Introduction to Conjoint Analysis and MaxDiff",
  "Survey Masterclass: Intensive Review of Best Practices for Online Surveys", 
  "Log Sequence Analysis: Tools to Visualize, Model, and Understand Instrument Logs",
  "Psychometrics for Survey Scales: Reliability and Validity Assessment for Practitioners",
  "R-Intensive: In-Person R Programming Bootcamp for Social Scientists in Industry",
  "The Price is Right: Best Practices in Pricing Research",
  "HEART UX Metrics Deep Dive: From Best Practices to Leading HEART Workshops with Your Team",
  "Introduction to Bayesian Statistics: Linear and Hierarchical Linear Bayesian Models in R",
  "Text Analytics 0 to 60: Sentiment Analysis and Topic Modeling with Natural Language Texts",
  "Yes, It is Causation, and not Correlation: Models for Causal Inference in R",
  "Interviewer Training: Improving Your Team's Quant UX Interview Process",
  "Advanced Choice Modeling Surveys: Advanced Options Beyond Standard Conjoint and MaxDiff",
  "Segmentation: Running a Successful Segmentation Effort, from the Models through Team Politics",
  "UX Metrics Sprintmaster Training: How to Lead UX Metrics Sprints"
)

# Create a mapping of long names to short names
name_mapping <- c(
  "Choice Modeling Hands-On: Introduction to Conjoint Analysis and MaxDiff" = "Choice Models",
  "Survey Masterclass: Intensive Review of Best Practices for Online Surveys" = "Surveys", 
  "Log Sequence Analysis: Tools to Visualize, Model, and Understand Instrument Logs" = "Log Sequences",
  "Psychometrics for Survey Scales: Reliability and Validity Assessment for Practitioners" = "Psychometrics",
  "R-Intensive: In-Person R Programming Bootcamp for Social Scientists in Industry" = "R Programming",
  "The Price is Right: Best Practices in Pricing Research" = "Pricing",
  "HEART UX Metrics Deep Dive: From Best Practices to Leading HEART Workshops with Your Team" = "UX Metrics",
  "Introduction to Bayesian Statistics: Linear and Hierarchical Linear Bayesian Models in R" = "Bayes Stats",
  "Text Analytics 0 to 60: Sentiment Analysis and Topic Modeling with Natural Language Texts" = "Text Analytics",
  "Yes, It is Causation, and not Correlation: Models for Causal Inference in R" = "Causal Models",
  "Interviewer Training: Improving Your Team's Quant UX Interview Process" = "Interviewer-ing",
  "Advanced Choice Modeling Surveys: Advanced Options Beyond Standard Conjoint and MaxDiff" = "Advanced Choice",
  "Segmentation: Running a Successful Segmentation Effort, from the Models through Team Politics" = "Segmentation",
  "UX Metrics Sprintmaster Training: How to Lead UX Metrics Sprints" = "Metrics Sprints"
)

# Calculate individual-level utility scores using tidyverse
llm_responses <- llm_responses |>
  mutate(
    user_id = str_c(model_name, persona_index, sep = "_"),
    model_clean = case_when(
      str_detect(tolower(model_name), "gpt") ~ "GPT",
      str_detect(tolower(model_name), "claude") ~ "Claude", 
      str_detect(tolower(model_name), "gemini") ~ "Gemini",
      TRUE ~ model_name
    )
  )

# convert numeric responses to strings for compatibility with brms
human_data_indiv_choices <- human_data_indiv_choices |>
  mutate(
    response = case_when(
      response == 1 ~ "best",
      response == -1 ~ "worst", 
      response == 0 ~ "neither"
    )
  )
```

# Convert LLM responses to long format

```{r convert_llm_responses_to_long}
library(tidyr)

# Create item lookup table from class_names
item_lookup <- tibble(
  item_name = as.character(class_names),
  item = 1:length(class_names)
)

# Function to format LLM responses to match human_data_indiv_choices structure
format_llm_to_individual_choices <- function(data) {
  
  formatted_data <- data |>
    mutate(original_row_id = row_number()) |>
    # Use pattern matching to find which class_names appear in each trial_items string
    rowwise() |>
    mutate(
      matched_items = list({
        matches <- character(0)
        for(class_name in as.character(class_names)) {
          if(str_detect(trial_items, fixed(class_name))) {
            matches <- c(matches, class_name)
          }
        }
        matches
      })
    ) |>
    ungroup() |>
    # Unnest to create separate rows for each matched item
    unnest(matched_items) |>
    # Join with item lookup table to get numeric item IDs
    left_join(item_lookup, by = c("matched_items" = "item_name")) |>
    # Strip names from item column to get just numeric values
    mutate(item = as.numeric(item)) |>
    # Create position within each original trial (1-5 for each original row)
    group_by(original_row_id) |>
    mutate(position = row_number()) |>
    ungroup() |>
    # Create response column based on best/worst item selections
    mutate(
      response = case_when(
        matched_items == best_item_name ~ 1,   # best choice gets 1
        matched_items == worst_item_name ~ -1, # worst choice gets -1
        TRUE ~ 0                               # not selected items get 0
      )
    ) |>
    # Select and rename columns to match human_data_indiv_choices format
    select(
      record_id = user_id,
      task = trial_number,
      position,
      item,
      response
    ) |>
    filter(!is.na(item)) |>
    arrange(record_id, task, position)
  
  return(formatted_data)
}

# Apply the transformation
llm_responses_formatted <- format_llm_to_individual_choices(llm_responses)
```

# Bayesian Modeling with LLM Data

```{r bayesian_llm_modeling}
library(afex)
afex::set_sum_contrasts()

# Prepare LLM data

# convert numeric responses to strings for compatibility with brms
llm_responses_formatted <- llm_responses_formatted |>
  mutate(
    response = case_when(
      response == 1 ~ "best",
      response == -1 ~ "worst", 
      response == 0 ~ "neither"
    )
  )

# factor conversion
llm_responses_formatted <- llm_responses_formatted |> mutate(across(everything(), factor))
llm_responses_formatted$item <- as.factor(unname(llm_responses_formatted$item)) # strip the names

# Construct the Bayesian model for LLM
model_llm <- brm(
  bf(response ~ 0 + item + (1 | ID | record_id)),
  data = llm_responses_formatted,
  family = categorical(refcat = "worst"),
  prior = c(
    prior(normal(0, 3), class = b, dpar = mubest),
    prior(normal(0, 3), class = b, dpar = muneither),
    prior(exponential(1), class = sd, dpar = mubest),
    prior(exponential(1), class = sd, dpar = muneither)
  ),
  chains = 4, cores = 4, iter = 2000, seed = 1234,
  backend = "cmdstanr", threads = threading(2),
  file = "model_llm",
  silent = FALSE
)
```

# Generate Priors from LLM Model
```{r generate_priors}
# Extract posterior draws for mubest coefficients
llm_mubest_draws <- model_llm |> 
  gather_draws(`^b_mubest_item.*$`, regex = TRUE)

# Extract posterior draws for muneither coefficients
llm_muneither_draws <- model_llm |> 
  gather_draws(`^b_muneither_item.*$`, regex = TRUE)

# Calculate mean and HDI for mubest coefficients
llm_mubest_priors_df <- llm_mubest_draws |>
  group_by(.variable) |>
  summarise(
    mean_est = mean(.value),
    mean_sd = sd(.value),
    #hdi_lower = hdi(.value)[1],
    #hdi_upper = hdi(.value)[2],
    #hdi_width = hdi_upper - hdi_lower,
    .groups = "drop"
  ) |>
  mutate(
    # Construct weakly informative prior mean and sd
    prior_mean = mean_est,
    prior_sd = mean_sd * 10#hdi_width * 2
  )

# Calculate mean and HDI for muneither coefficients
llm_muneither_priors_df <- llm_muneither_draws |>
  group_by(.variable) |>
  summarise(
    mean_est = mean(.value),
    mean_sd = sd(.value),
    #hdi_lower = hdi(.value)[1],
    #hdi_upper = hdi(.value)[2],
    #hdi_width = hdi_upper - hdi_lower,
    .groups = "drop"
  ) |>
  mutate(
    # Construct weakly informative prior mean and sd
    prior_mean = mean_est,
    prior_sd = mean_sd * 10#hdi_width
  )

# Create prior specifications for brms
priors <- NULL

# Add mubest priors
for(i in 1:nrow(llm_mubest_priors_df)) {
  coef_name <- str_remove(llm_mubest_priors_df$.variable[i], "b_mubest_")
  
  new_prior <- prior_string(paste0("normal(", llm_mubest_priors_df$prior_mean[i], ", ", llm_mubest_priors_df$prior_sd[i], ")"), 
                           class = "b", 
                           coef = coef_name,
                           dpar = "mubest")
  
  priors <- if(is.null(priors)) new_prior else priors + new_prior
}

# Add muneither priors
for(i in 1:nrow(llm_muneither_priors_df)) {
  coef_name <- str_remove(llm_muneither_priors_df$.variable[i], "b_muneither_")
  
  new_prior <- prior_string(paste0("normal(", llm_muneither_priors_df$prior_mean[i], ", ", llm_muneither_priors_df$prior_sd[i], ")"), 
                           class = "b", 
                           coef = coef_name,
                           dpar = "muneither")
  
  priors <- priors + new_prior
}

# Add priors for sd parameters
priors <- c(priors,
  prior(exponential(1), class = sd, dpar = mubest),
  prior(exponential(1), class = sd, dpar = muneither)
)
```

# Fit Omnibus Model with All Human Data (Run Once)

```{r omnibus_model}
# Fit the omnibus model with all human data
model_human_omnibus <- brm(
  bf(response ~ 0 + item + (1 | ID | record_id)),
  data = human_data_indiv_choices,
  family = categorical(refcat = "worst"),
  prior = c(
    prior(normal(0, 3), class = b, dpar = mubest),
    prior(normal(0, 3), class = b, dpar = muneither),
    prior(exponential(1), class = sd, dpar = mubest),
    prior(exponential(1), class = sd, dpar = muneither)
  ),
  chains = 4, cores = 4, iter = 2000, seed = 1234,
  backend = "cmdstanr", threads = threading(2),
  file = "model_human_omnibus",
  silent = FALSE
)

# Get omnibus model mubest coefficients (these remain constant across n_users loops)
omnibus_mubest <- fixef(model_human_omnibus)[grepl("mubest", rownames(fixef(model_human_omnibus))), "Estimate"]
names(omnibus_mubest) <- str_remove(names(omnibus_mubest), "mubest_")

# Get omnibus model mubest standard deviations
omnibus_mubest_sds <- fixef(model_human_omnibus)[grepl("mubest", rownames(fixef(model_human_omnibus))), "Est.Error"]
names(omnibus_mubest_sds) <- str_remove(names(omnibus_mubest_sds), "mubest_")

# Calculate mean SD for omnibus model
mean_sd_omnibus <- mean(omnibus_mubest_sds)

# Calculate LLM prior ranking correlation (constant across n_users loops)
prior_betas <- llm_mubest_priors_df |> arrange(nchar(.variable), .variable) |> select(.variable, mean_est)
prior_ranks <- rank(-prior_betas$mean_est)
names(prior_ranks) = names(omnibus_mubest)
omnibus_ranks <- rank(-omnibus_mubest)
cor_prior_ranks <- cor(omnibus_ranks, prior_ranks, method = "spearman")
```

# Loop Through Different Sample Sizes

```{r loop_through_n_users}
# Initialize storage for all results across different n_users
all_results <- list()

# Get unique user IDs once
user_ids <- unique(human_data_indiv_choices$record_id)

# Loop through each value of n_users
for (current_n_users in n_users) {
  
  cat("==============================================\n")
  cat("Starting analysis for n_users =", current_n_users, "\n")
  cat("==============================================\n")
  
  # Set up storage for this n_users value
  results_list_llm_prior <- list()
  results_list_flat_prior <- list()
  results_sds_llm_prior <- list()
  results_sds_flat_prior <- list()
  
  set.seed(1234)
  tic.clearlog()
  
  # Bayesian Modeling on Random Human Samples
  for (i in 1:n_simulations) {
    tic()
    # Sample current_n_users users
    random_user_ids <- sample(user_ids, current_n_users)
    sampled_data <- human_data_indiv_choices |>
      filter(record_id %in% random_user_ids)
    
    # Fit model with informative priors from LLM
    llm_informed_prior_model <- brm(
      formula = response ~ 0 + item + (1 | ID | record_id),
      data = sampled_data,
      family = categorical(refcat = "worst"),
      prior = priors,
      chains = 4, cores = 4, iter = 1000, seed = 1234,
      backend = "cmdstanr", threads = threading(2),
      refresh = 0,
      silent = 2
    )
    
    flat_prior_model <- brm(
      formula = response ~ 0 + item + (1 | ID | record_id),
      data = sampled_data,
      family = categorical(refcat = "worst"),
      chains = 4, cores = 4, iter = 1000, seed = 1234,
      backend = "cmdstanr", threads = threading(2),
      refresh = 0,
      silent = 2
    )
    
    # Extract mubest coefficients directly from the models
    mubest_coefs_llm_prior <- fixef(llm_informed_prior_model)[grepl("mubest", x = rownames(fixef(llm_informed_prior_model))), "Estimate"]
    results_list_llm_prior[[i]] <- mubest_coefs_llm_prior
    
    mubest_coefs_flat_prior <- fixef(flat_prior_model)[grepl("mubest", rownames(fixef(flat_prior_model))), "Estimate"]
    results_list_flat_prior[[i]] <- mubest_coefs_flat_prior
    
    # Extract mubest standard deviations from the models
    mubest_sds_llm_prior <- fixef(llm_informed_prior_model)[grepl("mubest", x = rownames(fixef(llm_informed_prior_model))), "Est.Error"]
    results_sds_llm_prior[[i]] <- mubest_sds_llm_prior
    
    mubest_sds_flat_prior <- fixef(flat_prior_model)[grepl("mubest", rownames(fixef(flat_prior_model))), "Est.Error"]
    results_sds_flat_prior[[i]] <- mubest_sds_flat_prior
    
    toc(log = TRUE, quiet = TRUE)
    
    # Progress indicator
    if (i %% 5 == 0) {
      cat("Completed", i, "of", n_simulations, "simulations for n_users =", current_n_users, "\n")
      
      # Get all timing data
      timing_log <- tic.log(format = FALSE)
      
      if (length(timing_log) > 0) {
        # Calculate total elapsed time for all iterations so far
        total_elapsed <- sum(sapply(timing_log, function(x) x$toc - x$tic))
        
        # Average time per iteration
        avg_time_per_iteration <- total_elapsed / i
        
        # Estimate remaining time
        remaining_time_minutes <- (n_simulations - i) * avg_time_per_iteration / 60
        
        cat("Avg per iteration:", round(avg_time_per_iteration, 1), "sec |", 
            "ETA:", round(remaining_time_minutes, 1), "min\n\n")
      }
    }
  }
  
  # Analysis of Results for current n_users
  cat("Analyzing results for n_users =", current_n_users, "\n")
  
  # Calculate Spearman correlations and top 5 item overlap for LLM prior
  sample_correlations_llm_prior <- sapply(results_list_llm_prior, function(sample_mubest) {
    # Ensure same ordering of items
    names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
    
    # Create rankings
    omnibus_ranks <- rank(-omnibus_mubest)
    sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
    
    # Calculate Spearman correlation
    cor(omnibus_ranks, sample_ranks, method = "spearman")
  })
  
  # Calculate mean SDs for LLM prior samples
  sample_sds_llm_prior <- sapply(results_sds_llm_prior, function(sample_sds) {
    return(mean(sample_sds))
  })
  
  # Calculate mean SD across all LLM prior samples
  mean_sd_llm_prior <- mean(sample_sds_llm_prior)
  
  top5_overlap_llm_prior <- sapply(results_list_llm_prior, function(sample_mubest) {
    # Ensure same ordering of items
    names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
    
    # Create rankings
    omnibus_ranks <- rank(-omnibus_mubest)
    sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
    
    # Get top 5 items for each ranking (highest ranks)
    omnibus_top5 <- names(sort(omnibus_ranks, decreasing = TRUE)[1:5])
    sample_top5 <- names(sort(sample_ranks, decreasing = TRUE)[1:5])
    
    # Calculate proportion of overlap
    overlap_count <- length(intersect(omnibus_top5, sample_top5))
    overlap_proportion <- overlap_count / 5
    
    return(overlap_proportion)
  })
  
  # Calculate Spearman correlations and top 5 item overlap for flat prior
  sample_correlations_flat_prior <- sapply(results_list_flat_prior, function(sample_mubest) {
    # Ensure same ordering of items
    names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
    
    # Create rankings
    omnibus_ranks <- rank(-omnibus_mubest)
    sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
    
    # Calculate Spearman correlation
    cor(omnibus_ranks, sample_ranks, method = "spearman")
  })
  
  # Calculate mean SDs for flat prior samples
  sample_sds_flat_prior <- sapply(results_sds_flat_prior, function(sample_sds) {
    return(mean(sample_sds))
  })
  
  # Calculate mean SD across all flat prior samples
  mean_sd_flat_prior <- mean(sample_sds_flat_prior)
  
  top5_overlap_flat_prior <- sapply(results_list_flat_prior, function(sample_mubest) {
    # Ensure same ordering of items
    names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
    
    # Create rankings
    omnibus_ranks <- rank(-omnibus_mubest)
    sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
    
    # Get top 5 items for each ranking (highest ranks)
    omnibus_top5 <- names(sort(omnibus_ranks, decreasing = TRUE)[1:5])
    sample_top5 <- names(sort(sample_ranks, decreasing = TRUE)[1:5])
    
    # Calculate proportion of overlap
    overlap_count <- length(intersect(omnibus_top5, sample_top5))
    overlap_proportion <- overlap_count / 5
    
    return(overlap_proportion)
  })
  
  # Calculate mean top 5 overlap proportions
  mean_top5_overlap_llm <- mean(top5_overlap_llm_prior)
  mean_top5_overlap_flat <- mean(top5_overlap_flat_prior)
  
  # Calculate probability that top human item is in top 5 LLM sets
  top_human_in_llm_top5 <- sapply(results_list_llm_prior, function(sample_mubest) {
    # Ensure same ordering of items
    names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
    
    # Create rankings
    omnibus_ranks <- rank(-omnibus_mubest)
    sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
    
    # Get top human item (highest rank)
    top_human_item <- names(which(omnibus_ranks == max(omnibus_ranks)))
    
    # Get top 5 LLM items
    sample_top5 <- names(sort(sample_ranks, decreasing = TRUE)[1:5])
    
    # Check if top human item is in top 5 LLM items
    as.numeric(top_human_item %in% sample_top5)
  })
  
  top_human_in_flat_top5 <- sapply(results_list_flat_prior, function(sample_mubest) {
    # Ensure same ordering of items
    names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
    
    # Create rankings
    omnibus_ranks <- rank(-omnibus_mubest)
    sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
    
    # Get top human item (highest rank)
    top_human_item <- names(which(omnibus_ranks == max(omnibus_ranks)))
    
    # Get top 5 flat prior items
    sample_top5 <- names(sort(sample_ranks, decreasing = TRUE)[1:5])
    
    # Check if top human item is in top 5 flat prior items
    as.numeric(top_human_item %in% sample_top5)
  })
  
  # Calculate probabilities
  prob_top_human_in_llm_top5 <- mean(top_human_in_llm_top5)
  prob_top_human_in_flat_top5 <- mean(top_human_in_flat_top5)
  
  # Calculate probability of exact top item match (single highest item)
  top_item_matches_llm_prior <- sapply(results_list_llm_prior, function(sample_mubest) {
    # Ensure same ordering of items
    names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
    
    # Create rankings
    omnibus_ranks <- rank(-omnibus_mubest)
    sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
    
    # Check if top-ranked items match (rank with highest value)
    omnibus_top <- names(which(omnibus_ranks == max(omnibus_ranks)))
    sample_top <- names(which(sample_ranks == max(sample_ranks)))
    
    # Return 1 if match, 0 if not
    as.numeric(omnibus_top == sample_top)
  })
  
  top_item_matches_flat_prior <- sapply(results_list_flat_prior, function(sample_mubest) {
    # Ensure same ordering of items
    names(sample_mubest) <- str_remove(names(sample_mubest), "mubest_")
    
    # Create rankings
    omnibus_ranks <- rank(-omnibus_mubest)
    sample_ranks <- rank(-sample_mubest[names(omnibus_mubest)])
    
    # Check if top-ranked items match
    omnibus_top <- names(which(omnibus_ranks == max(omnibus_ranks)))
    sample_top <- names(which(sample_ranks == max(sample_ranks)))
    
    # Return 1 if match, 0 if not
    as.numeric(omnibus_top == sample_top)
  })
  
  # Calculate probabilities of exact top item match
  prob_correct_llm <- mean(top_item_matches_llm_prior)
  prob_correct_flat <- mean(top_item_matches_flat_prior)
  
  # Statistical tests
  fisherZTest <- psych::r.test(n = n_simulations, r12 = mean(sample_correlations_llm_prior), r34 = mean(sample_correlations_flat_prior))
  fisherZTest_llm_0.7 <- psych::r.test(n = length(omnibus_mubest), r12 = mean(sample_correlations_llm_prior), r34 = 0.7)
  fisherZTest_flat_0.7 <- psych::r.test(n = length(omnibus_mubest), r12 = mean(sample_correlations_flat_prior), r34 = 0.7)
  
  # t-test for top 5 overlap
  top5_ttest <- t.test(top5_overlap_llm_prior, top5_overlap_flat_prior)
  
  # Proportion tests
  top_human_prop_test <- prop.test(c(sum(top_human_in_llm_top5), sum(top_human_in_flat_top5)),
                                   c(length(top_human_in_llm_top5), length(top_human_in_flat_top5)))
  
  exact_top_prop_test <- prop.test(c(sum(top_item_matches_llm_prior), sum(top_item_matches_flat_prior)),
                                   c(length(top_item_matches_llm_prior), length(top_item_matches_flat_prior)))
  
  # Store all results for this n_users value
  current_results <- list(
    n_users = current_n_users,
    sample_correlations_llm_prior = sample_correlations_llm_prior,
    sample_correlations_flat_prior = sample_correlations_flat_prior,
    mean_top5_overlap_llm = mean_top5_overlap_llm,
    mean_top5_overlap_flat = mean_top5_overlap_flat,
    prob_top_human_in_llm_top5 = prob_top_human_in_llm_top5,
    prob_top_human_in_flat_top5 = prob_top_human_in_flat_top5,
    prob_correct_llm = prob_correct_llm,
    prob_correct_flat = prob_correct_flat,
    mean_sd_llm_prior = mean_sd_llm_prior,
    mean_sd_flat_prior = mean_sd_flat_prior,
    fisherZTest = fisherZTest,
    fisherZTest_llm_0.7 = fisherZTest_llm_0.7,
    fisherZTest_flat_0.7 = fisherZTest_flat_0.7,
    top5_ttest = top5_ttest,
    top_human_prop_test = top_human_prop_test,
    exact_top_prop_test = exact_top_prop_test,
    results_list_llm_prior = results_list_llm_prior,
    results_list_flat_prior = results_list_flat_prior,
    results_sds_llm_prior = results_sds_llm_prior,
    results_sds_flat_prior = results_sds_flat_prior
  )
  
  # Add to overall results
  all_results[[paste0("n", current_n_users)]] <- current_results
  
  # Print summary for this n_users
  cat("\n=== SUMMARY FOR n_users =", current_n_users, "===\n")
  cat("LLM Prior - Mean correlation:", round(mean(sample_correlations_llm_prior), 3), "\n")
  cat("Flat Prior - Mean correlation:", round(mean(sample_correlations_flat_prior), 3), "\n")
  cat("Difference (LLM - Flat):", round(mean(sample_correlations_llm_prior) - mean(sample_correlations_flat_prior), 3), "\n")
  cat("Fisher Z test p-value:", round(fisherZTest$p, 4), "\n")
  cat("Mean top 5 overlap - LLM:", round(mean_top5_overlap_llm, 3), "| Flat:", round(mean_top5_overlap_flat, 3), "\n")
  cat("P(exact top match) - LLM:", round(prob_correct_llm, 3), "| Flat:", round(prob_correct_flat, 3), "\n\n")
  
  # Save only the essential objects for this specific n_users iteration
  # Include key constant objects needed for analysis
  save(
    # Current iteration results
    current_results,
    current_n_users,
    # Essential constant objects (needed for analysis/plotting)
    omnibus_mubest,
    omnibus_mubest_sds,
    mean_sd_omnibus,
    cor_prior_ranks,
    name_mapping,
    short_names,
    class_names,
    # Simulation parameters
    n_simulations,
    # Models (if you want to keep them, but they're large)
    # model_llm,
    # model_human_omnibus,
    file = paste0("n", current_n_users, ".RData")
  )
  cat("Results saved as n", current_n_users, ".RData\n\n")
  
  # Clean up iteration-specific variables to prevent accumulation
  rm(results_list_llm_prior, results_list_flat_prior, 
     results_sds_llm_prior, results_sds_flat_prior,
     sample_correlations_llm_prior, sample_correlations_flat_prior,
     sample_sds_llm_prior, sample_sds_flat_prior,
     mean_sd_llm_prior, mean_sd_flat_prior,
     top5_overlap_llm_prior, top5_overlap_flat_prior,
     mean_top5_overlap_llm, mean_top5_overlap_flat,
     top_human_in_llm_top5, top_human_in_flat_top5,
     prob_top_human_in_llm_top5, prob_top_human_in_flat_top5,
     top_item_matches_llm_prior, top_item_matches_flat_prior,
     prob_correct_llm, prob_correct_flat,
     fisherZTest, fisherZTest_llm_0.7, fisherZTest_flat_0.7,
     top5_ttest, top_human_prop_test, exact_top_prop_test)
  
  # Force garbage collection to free memory
  gc()
}

cat("==============================================\n")
cat("ALL SAMPLE SIZES COMPLETED!\n")
cat("==============================================\n")

# Save the complete results summary
save(all_results, 
     omnibus_mubest, omnibus_mubest_sds, mean_sd_omnibus, cor_prior_ranks,
     name_mapping, short_names, class_names, n_simulations, n_users,
     file = "all_results_summary.RData")
cat("Complete summary saved as all_results_summary.RData\n\n")
```

# Create Summary Visualization Across All Sample Sizes

```{r summary_visualization}
# Extract summary statistics across all n_users values
summary_df <- data.frame(
  n_users = sapply(all_results, function(x) x$n_users),
  mean_corr_llm = sapply(all_results, function(x) mean(x$sample_correlations_llm_prior)),
  mean_corr_flat = sapply(all_results, function(x) mean(x$sample_correlations_flat_prior)),
  median_corr_llm = sapply(all_results, function(x) median(x$sample_correlations_llm_prior)),
  median_corr_flat = sapply(all_results, function(x) median(x$sample_correlations_flat_prior)),
  sd_corr_llm = sapply(all_results, function(x) sd(x$sample_correlations_llm_prior)),
  sd_corr_flat = sapply(all_results, function(x) sd(x$sample_correlations_flat_prior)),
  top5_overlap_llm = sapply(all_results, function(x) x$mean_top5_overlap_llm),
  top5_overlap_flat = sapply(all_results, function(x) x$mean_top5_overlap_flat),
  prob_correct_llm = sapply(all_results, function(x) x$prob_correct_llm),
  prob_correct_flat = sapply(all_results, function(x) x$prob_correct_flat),
  fisher_z_pvalue = sapply(all_results, function(x) x$fisherZTest$p)
)

# Create visualization of correlation performance across sample sizes
library(ggplot2)

# Reshape data for plotting
summary_long <- summary_df %>%
  filter(n_users <= 90) |> 
  select(n_users, mean_corr_llm, mean_corr_flat, top5_overlap_llm, top5_overlap_flat, 
         prob_correct_llm, prob_correct_flat) %>%
  pivot_longer(cols = -n_users, 
               names_to = c("metric", "prior_type"), 
               names_pattern = "(.*)_(llm|flat)",
               values_to = "value") %>%
  mutate(
    metric = case_when(
      metric == "mean_corr" ~ "Mean Rank Correlation",
      metric == "top5_overlap" ~ "Top 5 Items Overlap Probability",
      metric == "prob_correct" ~ "Exact Top Item Match Probability"
    ),
    prior_type = case_when(
      prior_type == "llm" ~ "LLM Prior",
      prior_type == "flat" ~ "Flat Prior"
    )
  )

# Create the plot
summary_long$metric <- factor(summary_long$metric, 
                             levels = c("Mean Rank Correlation", 
                                       "Top 5 Items Overlap Probability", 
                                       "Exact Top Item Match Probability"))

performance_plot <- ggplot(summary_long, aes(x = n_users, y = value, color = prior_type, shape = prior_type)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  facet_wrap(~metric, scales = "free_y", ncol = 1) +
  scale_color_manual(name = "Prior Type",
                     values = c("LLM Prior" = "#E69F00", "Flat Prior" = "#0072B2")) +
  scale_shape_manual(name = "Prior Type",
                     values = c("LLM Prior" = 16, "Flat Prior" = 17)) +
  scale_x_continuous(breaks = c(3, 15, 30, 60, 90)) +
  scale_y_continuous(limits = c(0, 1)) +
  labs(
    x = "Sub-Sample Size",
    y = "",
    title = "Choice Alignment With Full Sample (n = 308) For Different Sub-Sample Sizes",
    subtitle = "Flat vs LLM-Informed Priors"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    plot.subtitle = element_text(size = 16),
    strip.text = element_text(size = 16, face = "bold"),
    legend.position = "bottom",
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 14), 
  )

print(performance_plot)

# Save the plot
  ggsave(filename = "performance_plot.png",
         plot = performance_plot, width = 12, height = 9, dpi = 300, bg = "white")

# Print final summary table
cat("\n=== FINAL SUMMARY ACROSS ALL SAMPLE SIZES ===\n")
print(summary_df)
```

# Generate Individual Plots for Each Sample Size

```{r individual_plots}
short_names <- as.character(name_mapping)
names(short_names) <- paste0("item", 1:length(name_mapping))

# Generate correlation plot for each n_users value
for (n_users_val in names(all_results)) {
  current_data <- all_results[[n_users_val]]
  
  # Create combined data frame for both prior types
  correlation_df <- tibble(
    rho = c(current_data$sample_correlations_llm_prior, current_data$sample_correlations_flat_prior),
    prior_type = rep(c("LLM Prior", "Flat Prior"), 
                     c(length(current_data$sample_correlations_llm_prior), 
                       length(current_data$sample_correlations_flat_prior)))
  )
  
  # Create the plot
correlation_plot <- ggplot(correlation_df, aes(x = rho)) +
  geom_density(aes(fill = prior_type), alpha = 0.3) +
  scale_fill_manual(name = "Prior Type",
                    labels = c("Flat Prior", "LLM-Informed Prior"), 
                    values = c("#E69F00", "#0072B2")) + 
  scale_color_manual(name = "Prior Type",
                    labels = c("Flat Prior", "LLM-Informed Prior"), 
                    values = c("#E69F00", "#0072B2")) + 
  geom_vline(data = correlation_df %>% 
               group_by(prior_type) %>% 
               summarise(median_rho = median(rho)), 
             aes(xintercept = median_rho, color = prior_type), 
             linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = cor_prior_ranks), color = "red", alpha = 0.2, 
             linetype = "solid", size = 1) +
  # Add horizontal labels for dashed lines
  geom_text(data = correlation_df %>% 
              group_by(prior_type) %>% 
              summarise(median_rho = median(rho)) %>%
              mutate(
                label = paste0("ρ=", sprintf("%.2f", median_rho)),
                hjust_val = ifelse(prior_type == "Flat Prior", 1.1, -0.1),  # Left of line for flat, right for LLM
                text_color = ifelse(prior_type == "Flat Prior", "#E69F00", "#0072B2")
              ),
            aes(x = median_rho, y = 14, label = label, hjust = hjust_val),
            color = correlation_df %>% 
              group_by(prior_type) %>% 
              summarise(median_rho = median(rho)) %>%
              mutate(text_color = ifelse(prior_type == "Flat Prior", "#E69F00", "#0072B2")) %>%
              pull(text_color),
            size = 4, fontface = "bold",
            inherit.aes = FALSE) +
  # Add text overlay
  geom_label(data = data.frame(x = 0.02, y = 11.2), 
             aes(x = x, y = y), 
             label = paste0("Mean SD of Estimates (Uncertainty):\nOmnibus = ",
                           round(mean_sd_omnibus, 3),
                           "\nLLM Prior = ",
                           round(current_data$mean_sd_llm_prior, 2),
                           "\nFlat Prior = ",
                           round(current_data$mean_sd_flat_prior, 2),
                           "\n\nMean % overlap (top 5 items):\nLLM Prior = ", 
                           round(current_data$mean_top5_overlap_llm, 2), 
                           "\nFlat Prior = ", 
                           round(current_data$mean_top5_overlap_flat, 2),
                           "\n\nMean P(top item in top 5):\nLLM Prior = ",
                           round(current_data$prob_top_human_in_llm_top5, 2),
                           "\nFlat Prior = ",
                           round(current_data$prob_top_human_in_flat_top5, 2),
                           "\n\nP(exact top item match):\nLLM Prior = ",
                           round(current_data$prob_correct_llm, 2),
                           "\nFlat Prior = ",
                           round(current_data$prob_correct_flat, 2)),
             hjust = 0, vjust = 1, size = 3.5, 
             color = "black", fontface = "bold",
             fill = "white", colour = "black", 
             label.padding = unit(0.3, "lines"),
             inherit.aes = FALSE) +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 15), breaks = seq(0, 15, 5)) +
  labs(
    x = "Spearman Correlation (ρ)",
    y = "Density",
    title = "Distributions of Sub-Sample Ranking Alignment with Full Sample by Prior Type",
    subtitle = paste0("n=", current_data$n_users, " human samples and full human dataset (n=308)"),
    caption = "Red line: LLM-based prior rank correlation with full sample. Dashed line: Correlation distribution medians for each model."
  ) +
  theme_minimal() +
  theme(
  plot.title = element_text(size = 20, face = "bold"),
  plot.subtitle = element_text(size = 16),
  strip.text = element_text(size = 16, face = "bold"),
  legend.position = "bottom",
  legend.text = element_text(size = 16),
  legend.title = element_text(size = 16),
  axis.title = element_text(size = 14),
  axis.text = element_text(size = 14),
  plot.caption = element_text(size = 12, color = "gray50", hjust = 0),
)
  
  print(correlation_plot)
  
  # Save the plot
  ggsave(filename = paste0("correlation_plot_", n_users_val, ".png"), 
         plot = correlation_plot, width = 12, height = 9, dpi = 300, bg = "white")
}

cat("Individual plots generated and saved for each sample size.\n")
cat("Final analysis complete!\n")
```