---
title: "MaxDiff Analysis: Human vs LLM Mixed Model Variability Investigation"
author: "Aaron Gardony <agardony@gmail.com>"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8, dpi = 300)
```

# Introduction

This notebook compares MaxDiff survey results between human UX researchers (N=308) and LLM-simulated responses using 103 UX researcher personas across 3 different large language models (GPT, Claude, Gemini) with N=309 LLM users total. Both datasets evaluate the same 14 potential UX research classes. This analysis used Hierarchical Bayesian Multinomial Models to model individual choice behavior between human and LLM users.

# Data Loading and Preparation

## Load Required Libraries

```{r libraries}
# Core tidyverse
library(tidyverse)
library(readxl)

# Visualization and styling
library(ggplot2)
library(ggtext)
library(patchwork)
library(scales)
library(viridis)

# Data manipulation and stats
library(broom)
library(janitor)

# Tables
library(kableExtra)
library(gt)

# Set ggplot theme
theme_set(theme_minimal(base_size = 12, base_family = "sans"))

# Define a color palette as a list
colors <- list(
  primary = "#2E86AB",
  secondary = "#A23B72", 
  accent = "#F18F01",
  neutral = "#C73E1D",
  success = "#06D6A0",
  light_gray = "#F8F9FA",
  medium_gray = "#6C757D",
  gpt_color = "#10A37F",      # OpenAI green
  claude_color = "#CC785C",    # Anthropic orange
  gemini_color = "#4285F4"     # Google blue
)
```

## Load Human Data (Original Study)

```{r load_human_data}
# Read Excel data with approach
human_data <- read_excel("../maxdiff_data/QUX Survey 2024 - Future Classes - MaxDiff Individual raw scores.xlsx") |>
  select(-Anchor) |>  # Remove anchor column
  clean_names()  # Clean column names

human_data_indiv_choices <- read_excel("../maxdiff_data/QUX Survey_ Spring '24 - MaxDiff_Future Programming Design & choices (1).xlsx") |> 
  clean_names()

# Assign friendly names using a named vector
column_mapping <- c(
  "Choice Models" = "choice_models",
  "Surveys" = "surveys", 
  "Log Sequences" = "log_sequences",
  "Psychometrics" = "psychometrics",
  "R Programming" = "r_programming",
  "Pricing" = "pricing",
  "UX Metrics" = "ux_metrics",
  "Bayes Stats" = "bayes_stats",
  "Text Analytics" = "text_analytics",
  "Causal Models" = "causal_models",
  "Interviewer-ing" = "interviewer_ing",
  "Advanced Choice" = "advanced_choice",
  "Segmentation" = "segmentation",
  "Metrics Sprints" = "metrics_sprints"
)

# Apply the mapping by position (columns 3-16)
names(human_data)[3:16] <- names(column_mapping)
names(human_data_indiv_choices$item) <- names(column_mapping[human_data_indiv_choices$item])


# Get class column names
human_class_cols <- names(human_data)[3:16]

# Data summary
cat("Human data dimensions:", dim(human_data), "\n")
cat("Number of respondents:", nrow(human_data), "\n")
cat("Number of items:", length(human_class_cols), "\n")
```

## Load and Process LLM Data with Model Splits

```{r load_llm_data}
# Read LLM responses data
llm_responses <- read_csv("../maxdiff_data/temp_0.8/maxdiff_responses.csv")

# Create a mapping of long names to short names
class_names<- c(
  "Choice Modeling Hands-On: Introduction to Conjoint Analysis and MaxDiff",
  "Survey Masterclass: Intensive Review of Best Practices for Online Surveys", 
  "Log Sequence Analysis: Tools to Visualize, Model, and Understand Instrument Logs",
  "Psychometrics for Survey Scales: Reliability and Validity Assessment for Practitioners",
  "R-Intensive: In-Person R Programming Bootcamp for Social Scientists in Industry",
  "The Price is Right: Best Practices in Pricing Research",
  "HEART UX Metrics Deep Dive: From Best Practices to Leading HEART Workshops with Your Team",
  "Introduction to Bayesian Statistics: Linear and Hierarchical Linear Bayesian Models in R",
  "Text Analytics 0 to 60: Sentiment Analysis and Topic Modeling with Natural Language Texts",
  "Yes, It is Causation, and not Correlation: Models for Causal Inference in R",
  "Interviewer Training: Improving Your Team's Quant UX Interview Process",
  "Advanced Choice Modeling Surveys: Advanced Options Beyond Standard Conjoint and MaxDiff",
  "Segmentation: Running a Successful Segmentation Effort, from the Models through Team Politics",
  "UX Metrics Sprintmaster Training: How to Lead UX Metrics Sprints"
)

# Create a mapping of long names to short names
name_mapping <- c(
  "Choice Modeling Hands-On: Introduction to Conjoint Analysis and MaxDiff" = "Choice Models",
  "Survey Masterclass: Intensive Review of Best Practices for Online Surveys" = "Surveys", 
  "Log Sequence Analysis: Tools to Visualize, Model, and Understand Instrument Logs" = "Log Sequences",
  "Psychometrics for Survey Scales: Reliability and Validity Assessment for Practitioners" = "Psychometrics",
  "R-Intensive: In-Person R Programming Bootcamp for Social Scientists in Industry" = "R Programming",
  "The Price is Right: Best Practices in Pricing Research" = "Pricing",
  "HEART UX Metrics Deep Dive: From Best Practices to Leading HEART Workshops with Your Team" = "UX Metrics",
  "Introduction to Bayesian Statistics: Linear and Hierarchical Linear Bayesian Models in R" = "Bayes Stats",
  "Text Analytics 0 to 60: Sentiment Analysis and Topic Modeling with Natural Language Texts" = "Text Analytics",
  "Yes, It is Causation, and not Correlation: Models for Causal Inference in R" = "Causal Models",
  "Interviewer Training: Improving Your Team's Quant UX Interview Process" = "Interviewer-ing",
  "Advanced Choice Modeling Surveys: Advanced Options Beyond Standard Conjoint and MaxDiff" = "Advanced Choice",
  "Segmentation: Running a Successful Segmentation Effort, from the Models through Team Politics" = "Segmentation",
  "UX Metrics Sprintmaster Training: How to Lead UX Metrics Sprints" = "Metrics Sprints"
)

# Calculate individual-level utility scores using tidyverse
llm_responses <- llm_responses |>
  mutate(
    user_id = str_c(model_name, persona_index, sep = "_"),
    model_clean = case_when(
      str_detect(tolower(model_name), "gpt") ~ "GPT",
      str_detect(tolower(model_name), "claude") ~ "Claude", 
      str_detect(tolower(model_name), "gemini") ~ "Gemini",
      TRUE ~ model_name
    )
  )

# Check model distribution
llm_responses |> 
  count(model_clean, model_name) |>
  arrange(model_clean) |>
  print()

# approach to calculate user-item scores
calc_user_item_scores <- function(responses_df) {
  # Get all unique items
  all_items <- responses_df |>
    select(best_item_name, worst_item_name) |>
    pivot_longer(everything(), values_to = "item_name") |>
    filter(!is.na(item_name)) |>
    distinct(item_name) |>
    pull(item_name)
  
  # Count best/worst selections
  best_counts <- responses_df |>
    filter(!is.na(best_item_name)) |>
    count(user_id, best_item_name, name = "best_count") |>
    rename(item_name = best_item_name)
  
  worst_counts <- responses_df |>
    filter(!is.na(worst_item_name)) |>
    count(user_id, worst_item_name, name = "worst_count") |>
    rename(item_name = worst_item_name)
  
  # Count appearances using map approach
  appearance_counts <- responses_df |>
    filter(!is.na(trial_items)) |>
    select(user_id, trial_items) |>
    crossing(item_name = all_items) |>
    mutate(
      appears = map2_lgl(trial_items, item_name, ~str_detect(.x, fixed(.y)))
    ) |>
    filter(appears) |>
    count(user_id, item_name, name = "appearance_count")
  
  # Combine all counts
  all_users <- unique(responses_df$user_id)
  
  results <- crossing(user_id = all_users, item_name = all_items) |>
    left_join(best_counts, by = c("user_id", "item_name")) |>
    left_join(worst_counts, by = c("user_id", "item_name")) |>
    left_join(appearance_counts, by = c("user_id", "item_name")) |>
    replace_na(list(best_count = 0, worst_count = 0, appearance_count = 0)) |>
    mutate(
      best_rate = if_else(appearance_count > 0, best_count / appearance_count, 0),
      worst_rate = if_else(appearance_count > 0, worst_count / appearance_count, 0),
      utility_score = best_rate - worst_rate
    )
  
  return(results)
}

# Calculate user-item scores for LLM data (preserving model info)
llm_user_scores <- calc_user_item_scores(llm_responses)

# Add model information back to scores
model_mapping <- llm_responses |>
  select(user_id, model_clean) |>
  distinct()

llm_user_scores <- llm_user_scores |>
  left_join(model_mapping, by = "user_id")

# approach to create wide format data
create_wide_format <- function(long_data, name_mapping, include_model = FALSE) {
  # Prepare the base data
  base_data <- long_data |>
    mutate(short_name = name_mapping[item_name]) |>
    filter(!is.na(short_name))
  
  # Handle column selection based on include_model flag
  if (include_model) {
    selected_data <- base_data |>
      select(user_id, short_name, utility_score, model_clean)
    id_cols <- c("user_id", "model_clean")
  } else {
    selected_data <- base_data |>
      select(user_id, short_name, utility_score)
    id_cols <- "user_id"
  }
  
  # Create wide format
  wide_data <- selected_data |>
    pivot_wider(
      names_from = short_name,
      values_from = utility_score,
      values_fill = 0,
      id_cols = all_of(id_cols)
    ) |>
    rename(Record.ID = user_id)
  
  return(wide_data)
}

# Create wide format data for all LLM models combined
llm_wide_all <- create_wide_format(llm_user_scores, name_mapping, include_model = TRUE)

# Create separate datasets for each model
llm_wide_gpt <- llm_user_scores |>
  filter(model_clean == "GPT") |>
  create_wide_format(name_mapping) 

llm_wide_claude <- llm_user_scores |>
  filter(model_clean == "Claude") |>
  create_wide_format(name_mapping)

llm_wide_gemini <- llm_user_scores |>
  filter(model_clean == "Gemini") |>
  create_wide_format(name_mapping)

# Remove model column from combined dataset for consistency
llm_wide_combined <- llm_wide_all |>
  select(-model_clean)

# Find common items between datasets
common_items <- intersect(human_class_cols, names(llm_wide_combined)[-1])

# Create aligned datasets with only common items
human_data_subset <- human_data |>
  select(record_id, all_of(common_items))

llm_wide_combined <- llm_wide_combined |>
  select(Record.ID, all_of(common_items))

llm_wide_gpt <- llm_wide_gpt |>
  select(Record.ID, all_of(common_items))

llm_wide_claude <- llm_wide_claude |>
  select(Record.ID, all_of(common_items))

llm_wide_gemini <- llm_wide_gemini |>
  select(Record.ID, all_of(common_items))

cat("\nDataset dimensions:\n")
cat("Human data:", dim(human_data_subset), "\n")
cat("LLM Combined:", dim(llm_wide_combined), "\n")
cat("GPT data:", dim(llm_wide_gpt), "\n")
cat("Claude data:", dim(llm_wide_claude), "\n")
cat("Gemini data:", dim(llm_wide_gemini), "\n")
```
# Convert LLM responses to long format

```{r convert_llm_responses_to_long}
library(tidyr)

# Create item lookup table from class_names
item_lookup <- tibble(
  item_name = as.character(class_names),
  item = 1:length(class_names)
)

# Function to format LLM responses to match human_data_indiv_choices structure
format_llm_to_individual_choices <- function(data) {
  
  formatted_data <- data %>%
    mutate(original_row_id = row_number()) %>%
    # Use pattern matching to find which class_names appear in each trial_items string
    rowwise() %>%
    mutate(
      matched_items = list({
        matches <- character(0)
        for(class_name in as.character(class_names)) {
          if(str_detect(trial_items, fixed(class_name))) {
            matches <- c(matches, class_name)
          }
        }
        matches
      })
    ) %>%
    ungroup() %>%
    # Unnest to create separate rows for each matched item
    unnest(matched_items) %>%
    # Join with item lookup table to get numeric item IDs
    left_join(item_lookup, by = c("matched_items" = "item_name")) %>%
    # Strip names from item column to get just numeric values
    mutate(item = as.numeric(item)) %>%
    # Create position within each original trial (1-5 for each original row)
    group_by(original_row_id) %>%
    mutate(position = row_number()) %>%
    ungroup() %>%
    # Create response column based on best/worst item selections
    mutate(
      response = case_when(
        matched_items == best_item_name ~ 1,   # best choice gets 1
        matched_items == worst_item_name ~ -1, # worst choice gets -1
        TRUE ~ 0                               # not selected items get 0
      )
    ) %>%
    # Select and rename columns to match human_data_indiv_choices format
    select(
      record_id = user_id,
      task = trial_number,
      position,
      item,
      response
    ) %>%
    filter(!is.na(item)) %>%
    arrange(record_id, task, position)
  
  return(formatted_data)
}

# Apply the transformation
llm_responses_formatted <- format_llm_to_individual_choices(llm_responses)
```

# Hierarchical Bayesian Multinomial Model - Human Data

```{r bayesian_mixed_modeling_human_responses}
library(afex)
library(brms)
library(cmdstanr)

afex::set_sum_contrasts()

# convert numeric responses to strings for compatibility with brms
human_data_indiv_choices <- human_data_indiv_choices %>%
  mutate(
    response = case_when(
      response == 1 ~ "best",
      response == -1 ~ "worst", 
      response == 0 ~ "neither"
    )
  )

# factor conversion
human_data_indiv_choices <- human_data_indiv_choices |> mutate(across(everything(), factor))
human_data_indiv_choices$item <- as.factor(unname(human_data_indiv_choices$item)) # strip the names


model_human_categorical_brms <- brm(
  bf(response ~ 0 + item + (0+item | ID | record_id)),
  data = human_data_indiv_choices,
  family = categorical(refcat = "worst"),
  prior = c(
    prior(normal(0, 3), class = b, dpar = mubest),
    prior(normal(0, 3), class = b, dpar = muneither),
    prior(exponential(1), class = sd, dpar = mubest),
    prior(exponential(1), class = sd, dpar = muneither)
  ),
  chains = 4, cores = 4, iter = 2000, seed = 1234,
  silent = 0,
  backend = "cmdstanr", threads = threading(2),# refresh = 0,
  file = "model_human_categorical_brms"
)

model_human_categorical_brms_null <- brm(
  bf(response ~ 0 + item),
  data = human_data_indiv_choices,
  family = categorical(refcat = "worst"),
  prior = c(
    prior(normal(0, 3), class = b, dpar = mubest),
    prior(normal(0, 3), class = b, dpar = muneither)
  ),
  chains = 4, cores = 4, iter = 2000, seed = 1234,
  backend = "cmdstanr", threads = threading(2),# refresh = 0,
  file = "model_human_categorical_brms_null",
  silent=0
)

model_human_categorical_brms <- add_criterion(model_human_categorical_brms, "loo")
model_human_categorical_brms_null <- add_criterion(model_human_categorical_brms_null, "loo")

loo_compare(model_human_categorical_brms, model_human_categorical_brms_null)
```

## Inspect Model

```{r inspect_human_bayes_models}
summary(model_human_categorical_brms)
posterior_summary(model_human_categorical_brms, robust = TRUE)
library(tidybayes)

(utilities_human <- fixef(model_human_categorical_brms)[grepl("mubest", rownames(fixef(model_human_categorical_brms))), "Estimate"])

# Extract mubest coefficients (utilities) with full posterior distributions
human_model_utilities <- model_human_categorical_brms %>% 
  gather_draws(`^b_mubest_.*$`, regex = TRUE) %>% 
  # Clean up variable names by removing the "b_mubest_" prefix
  mutate(.variable = str_remove(.variable, "^b_mubest_"))

# Create the plot
human_model_utilities %>% 
  ggplot(aes(x = .value, y = .variable)) +
  stat_halfeye() +
  labs(
    x = "Posterior distribution of utilities (logit-scale)", 
    y = "Items",
    title = "Item Utilities: Preference for Being Chosen as Best"
  ) +
  theme_minimal()


# Extract random slopes for each user/item combo
human_model_random_slopes <- model_human_categorical_brms %>% 
  gather_draws(`^r_record_id__mubest\\[.*,.*\\]$`, regex = TRUE) %>% 
  # Clean up variable names to extract user IDs and item names
  separate_wider_regex(
    .variable,
    patterns = c(
      "r_record_id__mubest\\[", 
      user_id = "[^,]+", 
      ",",
      item_name = "[^\\]]+",
      "\\]"
    )
  )

human_model_fixed_effects <- model_human_categorical_brms %>% 
  gather_draws(`^b_mubest_item\\d+$`, regex = TRUE) %>% 
  # Clean up variable names to extract item names
  separate_wider_regex(
    .variable,
    patterns = c(
      "b_mubest_", 
      item_name = "item\\d+"
    )
  )

# Overall distribution of random slopes across all users
human_model_random_slopes %>%
  ggplot(aes(x = .value)) +
  geom_density(alpha = 0.7, fill = "steelblue") +
  labs(
    x = "Random slope values", 
    y = "Density",
    title = "Distribution of Individual Human User Random Slope Posterior Draws"
  ) +
  facet_wrap(~item_name, ncol = 4) +
  theme_minimal()

# Overall distribution of fixed effects across users
human_model_fixed_effects |> 
  ggplot(aes(x = .value)) +
  geom_density(alpha = 0.7, fill = "steelblue") +
  labs(
    x = "Fixed effect vaues", 
    y = "Density",
    title = "Distribution of Fixed Effect Posterior Draws"
  ) +
  facet_wrap(~item_name, ncol = 4) +
  theme_minimal()
```

# Hierarchical Bayesian Multinomial Model - LLM Data

```{r bayesian_mixed_modeling_llm_responses}
library(brms)
library(cmdstanr)

# convert numeric responses to strings for compatibility with brms
llm_responses_formatted <- llm_responses_formatted %>%
  mutate(
    response = case_when(
      response == 1 ~ "best",
      response == -1 ~ "worst", 
      response == 0 ~ "neither"
    )
  )

# factor conversion
llm_responses_formatted <- llm_responses_formatted |> mutate(across(everything(), factor))
llm_responses_formatted$item <- as.factor(unname(llm_responses_formatted$item)) # strip the names

afex::set_sum_contrasts()

model_llm_categorical_brms <- brm(
  bf(response ~ 0 + item + (0 + item | ID | record_id)),
  data = llm_responses_formatted,
  family = categorical(refcat = "worst"),
  prior = c(
    prior(normal(0, 3), class = b, dpar = mubest),
    prior(normal(0, 3), class = b, dpar = muneither),
    prior(exponential(1), class = sd, dpar = mubest),
    prior(exponential(1), class = sd, dpar = muneither)
  ),
  chains = 4, cores = 4, iter = 2000, seed = 1234,
  backend = "cmdstanr",threads = threading(2),# refresh = 0,
  file = "model_llm_categorical_brms",
  silent = 0
)

model_llm_categorical_brms_null <- brm(
  bf(response ~ 0 + item),
  data = llm_responses_formatted,
  family = categorical(refcat = "worst"),
  prior = c(
    prior(normal(0, 3), class = b, dpar = mubest),
    prior(normal(0, 3), class = b, dpar = muneither)
  ),
  chains = 4, cores = 4, iter = 2000, seed = 1234,
  backend = "cmdstanr", threads = threading(2),# refresh = 0,
  file = "model_llm_categorical_brms_null",
  silent = 0
)
model_llm_categorical_brms <- add_criterion(model_llm_categorical_brms, "loo")
model_llm_categorical_brms_null <- add_criterion(model_llm_categorical_brms_null, "loo")

loo_compare(model_llm_categorical_brms, model_llm_categorical_brms_null)
```

# Inspect Model

```{r inspect_llm_bayes_models}
summary(model_llm_categorical_brms)
posterior_summary(model_llm_categorical_brms, robust = TRUE)
library(tidybayes)

(utilities_human <- fixef(model_llm_categorical_brms)[grepl("mubest", rownames(fixef(model_llm_categorical_brms))), "Estimate"])

# Extract mubest coefficients (utilities) with full posterior distributions
llm_model_utilities <- model_llm_categorical_brms %>% 
  gather_draws(`^b_mubest_.*$`, regex = TRUE) %>% 
  # Clean up variable names by removing the "b_mubest_" prefix
  mutate(.variable = str_remove(.variable, "^b_mubest_"))

# Create the plot
llm_model_utilities %>% 
  ggplot(aes(x = .value, y = .variable)) +
  stat_halfeye() +
  labs(
    x = "Posterior distribution of utilities (logit-scale)", 
    y = "Items",
    title = "Item Utilities: Preference for Being Chosen as Best"
  ) +
  theme_minimal()


# Extract random slopes for each user/item combo
llm_model_random_slopes <- model_llm_categorical_brms %>% 
  gather_draws(`^r_record_id__mubest\\[.*,.*\\]$`, regex = TRUE) %>% 
  # Clean up variable names to extract user IDs and item names
  separate_wider_regex(
    .variable,
    patterns = c(
      "r_record_id__mubest\\[", 
      user_id = "[^,]+", 
      ",",
      item_name = "[^\\]]+",
      "\\]"
    )
  )

llm_model_fixed_effects <- model_llm_categorical_brms %>% 
  gather_draws(`^b_mubest_item\\d+$`, regex = TRUE) %>% 
  # Clean up variable names to extract item names
  separate_wider_regex(
    .variable,
    patterns = c(
      "b_mubest_", 
      item_name = "item\\d+"
    )
  )

# Overall distribution of random slopes across all LLM users
llm_model_random_slopes %>%
  ggplot(aes(x = .value)) +
  geom_density(alpha = 0.7, fill = "steelblue") +
  labs(
    x = "Random slope values", 
    y = "Density",
    title = "Distribution of Individual LLM User Random Slope Posterior Draws"
  ) +
  facet_wrap(~item_name, ncol = 4) +
  theme_minimal()

# Overall distribution of fixed effects across users
llm_model_fixed_effects |> 
  ggplot(aes(x = .value)) +
  geom_density(alpha = 0.7, fill = "steelblue") +
  labs(
    x = "Fixed effect vaues", 
    y = "Density",
    title = "Distribution of Fixed Effect Posterior Draws"
  ) +
  facet_wrap(~item_name, ncol = 4) +
  theme_minimal()


```

# Plot Fixed and Random Effects

```{r}
list(human_model_fixed_effects, llm_model_fixed_effects) %>%
  set_names(c("human", "llm")) %>%
  bind_rows(.id = "user_type") -> combined_fixed_effect_posterior_draws

short_names <- as.character(name_mapping)
names(short_names) <- paste0("item", 1:length(name_mapping))

combined_fixed_effect_posterior_draws %>%
  # Create ordered factor with short names
  mutate(
    item_short = short_names[item_name],
    item_short = factor(item_short, 
                       levels = short_names[paste0("item", 1:14)])  # Adjust number as needed
  ) |>
  ggplot(aes(x = .value, color = user_type, fill = user_type)) +
  geom_density(alpha = 0.1, position = "stack") +
  facet_wrap(~item_short, ncol = 4) +  # Use item_short instead of item_name
  xlab("Fixed Effect Posterior Distribution") + 
  scale_color_manual(name = "User Type",
                    labels = c("Human", "AI"), 
                    values = c("#E69F00", "#0072B2")) +
  scale_fill_manual(name = "User Type",
                    labels = c("Human", "AI"), 
                    values = c("#E69F00", "#0072B2"))

combined_fixed_effect_posterior_draws %>%
    # Create ordered factor with short names
    mutate(
        item_short = short_names[item_name],
        item_short = factor(item_short, 
                            levels = short_names[paste0("item", 1:14)])  # Adjust number as needed
    ) |>
    group_by(user_type, item_short) |> 
    summarize(var_eff = var(.value)) |>
  ggplot(aes(x = item_short, y = var_eff, fill = user_type, color = user_type)) + 
  geom_col(position = "dodge") + 
  scale_color_manual(name = "User Type",
                    labels = c("Human", "AI"), 
                    values = c("#E69F00", "#0072B2")) +
  scale_fill_manual(name = "User Type",
                    labels = c("Human", "AI"), 
                    values = c("#E69F00", "#0072B2"))


##### Production Charts ##### 

# Chart 1: Between-User Variability (Fixed Effects)
p1 <- combined_fixed_effect_posterior_draws %>%
  mutate(
    item_short = short_names[item_name],
    item_short = factor(item_short, 
                       levels = short_names[paste0("item", 1:14)])
  ) |>
  ggplot(aes(x = .value, fill = user_type)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~item_short, ncol = 4, scales = "free") +
  labs(
    title = "How Does Human and LLM Users' Item Choice Behavior Differ on Average?",
    subtitle = "Posterior distributions of item fixed effects (aggregated across users)",
    x = "Average Choice Effect (Across Users)",
    y = "",
    fill = "User Type",
    caption = "Larger numbers indicate greater preference; spread indicates aggregated preference variability."
  ) +
  scale_fill_manual(
    labels = c("Human", "AI"), 
    values = c("#E69F00", "#0072B2")
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11, color = "gray30"),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom",
    plot.caption = element_text(size = 9, color = "gray50", hjust = 0),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

# Chart 2: Within-User Variability (Random Slopes)
p2 <- combined_random_slopes_posterior_draws %>%
  mutate(
    item_short = short_names[item_name],
    item_short = factor(item_short, 
                       levels = short_names[paste0("item", 1:14)])
  ) |>
  group_by(user_type, user_id, item_short) |> 
  summarize(var_eff = var(.value), .groups = "drop") |>
  ggplot(aes(x = var_eff, fill = user_type, color = user_type)) + 
  geom_density(aes(y = after_stat(scaled)), alpha = 0.6) + 
  facet_wrap(~item_short, ncol = 4, scales = "free_x") +
  labs(
  title = "How Internally Consistent Is Each User's Responses?", 
  subtitle = "Distribution of by-user variances of choice item random slopes (one variance per user-item combo)",
  x = "Within-User Internal Response Variance",
  y = "",
  fill = "User Type",
  color = "User Type",
  caption = "Higher values indicated greater internal response variability."
) +
  scale_color_manual(
    name = "User Type",
    labels = c("Human", "AI"), 
    values = c("#E69F00", "#0072B2")
  ) +
  scale_fill_manual(
    name = "User Type",
    labels = c("Human", "AI"), 
    values = c("#E69F00", "#0072B2")
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 11, color = "gray30"),
    strip.text = element_text(size = 10, face = "bold"),
    legend.position = "bottom",
    plot.caption = element_text(size = 9, color = "gray50", hjust = 0),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

p1
p2



##### Production Charts ##### 

```

# Unused stuff (early drafts)

```{r unused_analyses}
# human
overall_slope_variance_human <- human_model_random_slopes %>%
    group_by(user_id) %>%
    summarise(
        total_slope_variance = var(.value),
        total_slope_sd = sd(.value)
    ) %>%
    summarise(
        mean_variance = mean(total_slope_variance),
        mean_sd = mean(total_slope_sd)
    )

slope_variance_by_item_human <- human_model_random_slopes %>%
    group_by(item_name, user_id) %>%
    summarise(
        slope_variance = var(.value),
        slope_sd = sd(.value),
        .groups = "drop"
    ) %>%
    # Summarize across posterior draws
    group_by(item_name) %>%
    summarise(
        mean_variance = mean(slope_variance),
        mean_sd = mean(slope_sd),
        .groups = "drop"
    )

mean_slope_variance_human_by_item <- human_model_random_slopes %>%
    group_by(user_id, item_name) |> 
    summarize(
        #slope_variance = var(.value),
        slope_sd = sd(.value)
    ) |> 
  group_by(item_name) |> 
    summarize(
        #mean_variance = mean(slope_variance),
        mean_sd = mean(slope_sd)
    ) |> arrange(nchar(item_name), item_name)

# llm
mean_slope_variance_llm_by_item <- llm_model_random_slopes %>%
    group_by(user_id, item_name) |> 
    summarise(
        #slope_variance = var(.value),
        slope_sd = sd(.value)
    ) |> 
  group_by(item_name) |> 
    summarize(
        #mean_variance = mean(slope_variance),
        mean_sd = mean(slope_sd)
    ) |> arrange(nchar(item_name), item_name)

slope_variance_by_item_llm <- llm_model_random_slopes %>%
    group_by(item_name, user_id) %>%
    summarise(
        slope_variance = var(.value),
        slope_sd = sd(.value),
        .groups = "drop"
    ) %>%
    # Summarize across posterior draws
    group_by(item_name) %>%
    summarise(
        mean_variance = mean(slope_variance),
        mean_sd = mean(slope_sd),
        .groups = "drop"
    )

(overall_slope_variance_human)
(slope_variance_by_item_human)
(overall_slope_variance_llm)
(slope_variance_by_item_llm)

llm_to_hum_var_ratio_by_item <- bind_cols(item = slope_variance_by_item_human$item_name, llm_to_human_var_ratio = slope_variance_by_item_llm$mean_variance/slope_variance_by_item_human$mean_variance) |> 
  arrange(nchar(item), item) |> bind_cols(class_name = class_names) |> 
  arrange(llm_to_human_var_ratio)

list(human_model_random_slopes, llm_model_random_slopes) %>%
  set_names(c("human", "llm")) %>%
  bind_rows(.id = "user_type") -> combined_posterior_random_slope_draws



short_names <- as.character(name_mapping)
names(short_names) <- paste0("item", 1:length(name_mapping))

combined_posterior_random_slope_draws %>%
  group_by(user_type, item_name) |> 
  mutate(slope_var_by_item = var(.value),
         slope_sd_by_item = sd(.value)) |> 
  ungroup() |> 
  group_by(user_type, item_name, user_id) %>%
  summarize(
    user_slope_variance = var(.value),
    user_slope_sd = sd(.value),
    slope_variance_within_between_groups_ratio = var(.value)/max(slope_var_by_item),
    slope_sd_within_between_groups_ratio = sd(.value)/max(slope_sd_by_item),
    .groups = "drop"
  ) |> 
  # Create ordered factor with short names
  mutate(
    item_short = short_names[item_name],
    item_short = factor(item_short, 
                       levels = short_names[paste0("item", 1:14)])  # Adjust number as needed
  ) |>
  ggplot(aes(x = (slope_variance_within_between_groups_ratio), fill = user_type)) +
  geom_density(aes(y = after_stat(scaled)), alpha = 0.5) +
  facet_wrap(~item_short, ncol = 4, scales = "free_y") +  # Use item_short instead of item_name
  xlab("Individual/Collective Choice Variance Ratio (Larger = More Human?)") + 
  labs(fill = "User Type") +
  scale_fill_manual(labels = c("Human", "AI"), 
                    values = c("#E69F00", "#0072B2"))



human_best_choice_fix_effects <- fixef(model_human_categorical_brms) |>
  as.data.frame() |> 
  rownames_to_column() |>
  mutate(item = rowname) |> 
  filter(str_detect(item, 'mubest_item')) |>
  select(item, Est.Error) |> 
  mutate(across('item', str_replace, 'mubest_', ''))

human_best_choice_ran_effect_errors <- ranef(model_human_categorical_brms) |>
  as.data.frame() |> 
  rownames_to_column() |> 
  select(rowname, contains("Est.Error.mubest_item")) |> 
  rename_with(~ sub(".*_", "", .)) |> 
  mutate(user_id = rowname, .before = 1) |> 
  select(-rowname) |> 
  pivot_longer(cols = starts_with("item"), names_to = "item", values_to = "error")

merged_human_choice_errors <- human_best_choice_ran_effect_errors |> 
  left_join(human_best_choice_fix_effects)


#######
llm_best_choice_fix_effects <- fixef(model_llm_categorical_brms) |>
  as.data.frame() |> 
  rownames_to_column() |>
  mutate(item = rowname) |> 
  filter(str_detect(item, 'mubest_item')) |>
  select(item, Est.Error) |> 
  mutate(across('item', str_replace, 'mubest_', ''))

llm_best_choice_ran_effect_errors <- ranef(model_llm_categorical_brms) |>
  as.data.frame() |> 
  rownames_to_column() |> 
  select(rowname, contains("Est.Error.mubest_item")) |> 
  rename_with(~ sub(".*_", "", .)) |> 
  mutate(user_id = rowname, .before = 1) |> 
  select(-rowname) |> 
  pivot_longer(cols = starts_with("item"), names_to = "item", values_to = "error")

merged_llm_choice_errors <- llm_best_choice_ran_effect_errors |> 
  left_join(llm_best_choice_fix_effects)

merged_llm_choice_errors |> 
  group_by(item) |> 
  ggplot(aes(x = error)) +
  geom_density(aes(y = after_stat(scaled)), alpha = 0.5) +
  facet_wrap(~item, ncol = 4, scales = "free_y") +
  xlab("CAPTION") +
  geom_vline(data = . %>% group_by(item) %>% summarise(Est.Error = first(Est.Error)), 
             aes(xintercept = Est.Error))

list(merged_human_choice_errors, merged_llm_choice_errors) %>%
  set_names(c("human", "llm")) %>%
  bind_rows(.id = "user_type") -> combined_choice_errors

short_names <- as.character(name_mapping)
names(short_names) <- paste0("item", 1:length(name_mapping))

combined_choice_errors %>%
  group_by(user_type, item, user_id) %>%
  # Create ordered factor with short names
  mutate(
    item_short = short_names[item],
    item_short = factor(item_short, 
                       levels = short_names[paste0("item", 1:14)])  # Adjust number as needed
  ) |>
  ggplot(aes(x = (Est.Error), fill = user_type)) +
  geom_density(aes(y = after_stat(scaled)), alpha = 0.5) +
  facet_wrap(~item_short, ncol = 4, scales = "free_y") +  # Use item_short instead of item_name
  xlab("CAPTION") + 
  labs(fill = "User Type") +
  scale_fill_manual(labels = c("Human", "AI"), 
                    values = c("#E69F00", "#0072B2"))

  
```