---
title: "MaxDiff Analysis: Cluster-Based Stratification"
author: "Aaron Gardony <agardony@gmail.com>"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
  html_notebook:
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8, dpi = 300)
```

# Introduction

This notebook analyzes MaxDiff survey results for LLM-simulated UX researcher responses (N=309) across five different cluster dimensions. The analysis focuses on how utility scores for 14 UX research classes vary across different persona clusters, examining patterns within cluster stratifications rather than comparing to human baselines.

**Key Analysis Dimensions:**
- **Seniority Clusters**: Career level segmentation  
- **Industry Clusters**: Domain-specific expertise areas
- **Expertise Clusters**: Research methodology specializations
- **Priorities Clusters**: Professional focus areas
- **Challenges Clusters**: Common workplace obstacles

# Data Loading and Preparation

## Load Required Libraries

```{r libraries}
# Core tidyverse
library(tidyverse)
library(readxl)

# Visualization and styling
library(ggplot2)
library(ggtext)
library(patchwork)
library(scales)
library(viridis)

# Data manipulation and stats
library(broom)
library(janitor)

# Tables
library(kableExtra)
library(gt)

# Set ggplot theme
theme_set(theme_minimal(base_size = 12, base_family = "sans"))

# Define a color palette as a list
colors <- list(
  primary = "#2E86AB",
  secondary = "#A23B72", 
  accent = "#F18F01",
  neutral = "#C73E1D",
  success = "#06D6A0",
  light_gray = "#F8F9FA",
  medium_gray = "#6C757D"
)
```

## Load and Process LLM Data with Clusters

```{r load_data}
# Read LLM responses data with cluster assignments
llm_responses <- read_csv("../persona_clustering/maxdiff_responses_with_clusters.csv")

# Create a mapping of long names to short names
name_mapping <- c(
  "Choice Modeling Hands-On: Introduction to Conjoint Analysis and MaxDiff" = "Choice Models",
  "Survey Masterclass: Intensive Review of Best Practices for Online Surveys" = "Surveys", 
  "Log Sequence Analysis: Tools to Visualize, Model, and Understand Instrument Logs" = "Log Sequences",
  "Psychometrics for Survey Scales: Reliability and Validity Assessment for Practitioners" = "Psychometrics",
  "R-Intensive: In-Person R Programming Bootcamp for Social Scientists in Industry" = "R Programming",
  "The Price is Right: Best Practices in Pricing Research" = "Pricing",
  "HEART UX Metrics Deep Dive: From Best Practices to Leading HEART Workshops with Your Team" = "UX Metrics",
  "Introduction to Bayesian Statistics: Linear and Hierarchical Linear Bayesian Models in R" = "Bayes Stats",
  "Text Analytics 0 to 60: Sentiment Analysis and Topic Modeling with Natural Language Texts" = "Text Analytics",
  "Yes, It is Causation, and not Correlation: Models for Causal Inference in R" = "Causal Models",
  "Interviewer Training: Improving Your Team's Quant UX Interview Process" = "Interviewer-ing",
  "Advanced Choice Modeling Surveys: Advanced Options Beyond Standard Conjoint and MaxDiff" = "Advanced Choice",
  "Segmentation: Running a Successful Segmentation Effort, from the Models through Team Politics" = "Segmentation",
  "UX Metrics Sprintmaster Training: How to Lead UX Metrics Sprints" = "Metrics Sprints"
)

# Add user ID for tracking
llm_responses <- llm_responses %>%
  mutate(user_id = str_c(model_name, persona_index, sep = "_"))

# Define cluster columns
cluster_columns <- c("seniority_cluster", "industry_cluster", "expertise_cluster", 
                    "priorities_cluster", "challenges_cluster")

# Check cluster distributions
cat("Cluster dimension overview:\n")
for (col in cluster_columns) {
  cat("\n", str_to_title(str_remove(col, "_cluster")), "Clusters:\n")
  cluster_counts <- llm_responses %>% 
    count(.data[[col]], name = "n_personas") %>%
    arrange(desc(n_personas))
  
  print(cluster_counts)
}
```

# Utility Score Calculation

## Function to Calculate User-Item Scores

```{r utility_functions}
# Function to calculate individual utility scores
calc_user_item_scores <- function(responses_df) {
  # Get all unique items
  all_items <- responses_df %>%
    select(best_item_name, worst_item_name) %>%
    pivot_longer(everything(), values_to = "item_name") %>%
    filter(!is.na(item_name)) %>%
    distinct(item_name) %>%
    pull(item_name)
  
  # Count best/worst selections
  best_counts <- responses_df %>%
    filter(!is.na(best_item_name)) %>%
    count(user_id, best_item_name, name = "best_count") %>%
    rename(item_name = best_item_name)
  
  worst_counts <- responses_df %>%
    filter(!is.na(worst_item_name)) %>%
    count(user_id, worst_item_name, name = "worst_count") %>%
    rename(item_name = worst_item_name)
  
  # Count appearances using map approach
  appearance_counts <- responses_df %>%
    filter(!is.na(trial_items)) %>%
    select(user_id, trial_items) %>%
    crossing(item_name = all_items) %>%
    mutate(
      appears = map2_lgl(trial_items, item_name, ~str_detect(.x, fixed(.y)))
    ) %>%
    filter(appears) %>%
    count(user_id, item_name, name = "appearance_count")
  
  # Combine all counts
  all_users <- unique(responses_df$user_id)
  
  results <- crossing(user_id = all_users, item_name = all_items) %>%
    left_join(best_counts, by = c("user_id", "item_name")) %>%
    left_join(worst_counts, by = c("user_id", "item_name")) %>%
    left_join(appearance_counts, by = c("user_id", "item_name")) %>%
    replace_na(list(best_count = 0, worst_count = 0, appearance_count = 0)) %>%
    mutate(
      best_rate = if_else(appearance_count > 0, best_count / appearance_count, 0),
      worst_rate = if_else(appearance_count > 0, worst_count / appearance_count, 0),
      utility_score = best_rate - worst_rate
    )
  
  return(results)
}

# Function to create wide format with cluster information
create_wide_format <- function(long_data, name_mapping, include_cluster = FALSE, cluster_name = NULL) {
  # Prepare the base data
  base_data <- long_data %>%
    mutate(short_name = name_mapping[item_name]) %>%
    filter(!is.na(short_name))
  
  # Handle column selection based on include_cluster flag
  if (include_cluster && !is.null(cluster_name)) {
    selected_data <- base_data %>%
      select(user_id, short_name, utility_score, all_of(cluster_name))
    id_cols <- c("user_id", cluster_name)
  } else {
    selected_data <- base_data %>%
      select(user_id, short_name, utility_score)
    id_cols <- "user_id"
  }
  
  # Create wide format
  wide_data <- selected_data %>%
    pivot_wider(
      names_from = short_name,
      values_from = utility_score,
      values_fill = 0,
      id_cols = all_of(id_cols)
    ) %>%
    rename(Record.ID = user_id)
  
  return(wide_data)
}

# Calculate user-item scores
llm_user_scores <- calc_user_item_scores(llm_responses)

# Add cluster information to user scores
cluster_info <- llm_responses %>%
  select(user_id, all_of(cluster_columns)) %>%
  distinct()

llm_user_scores <- llm_user_scores %>%
  left_join(cluster_info, by = "user_id")

cat("Utility scores calculated for", n_distinct(llm_user_scores$user_id), "users and", 
    n_distinct(llm_user_scores$item_name), "items\n")
```

# Cluster-Based Analysis

## Create Wide Format Data for Each Cluster Dimension

```{r create_wide_formats}
# Create wide format datasets for each cluster dimension
llm_wide_formats <- list()

for (cluster_col in cluster_columns) {
  cluster_name <- str_remove(cluster_col, "_cluster")
  llm_wide_formats[[cluster_name]] <- create_wide_format(
    llm_user_scores, 
    name_mapping, 
    include_cluster = TRUE, 
    cluster_name = cluster_col
  )
}

# Also create overall format without clusters
llm_wide_formats[["overall"]] <- create_wide_format(llm_user_scores, name_mapping)

# Get item column names from the wide format
item_cols <- names(llm_wide_formats[["overall"]])[-1]  # Exclude Record.ID

cat("Wide format datasets created for", length(llm_wide_formats), "cluster dimensions\n")
cat("Items included:", paste(item_cols, collapse = ", "), "\n")
```

## Calculate Cluster Means

```{r cluster_means}
# Function to calculate means for each cluster
calc_cluster_means <- function(cluster_name) {
  wide_data <- llm_wide_formats[[cluster_name]]
  cluster_col <- paste0(cluster_name, "_cluster")
  
  # Get the item columns (exclude Record.ID and cluster column)
  item_cols <- setdiff(names(wide_data), c("Record.ID", cluster_col))
  
  # Calculate means by cluster
  wide_data %>%
    group_by(.data[[cluster_col]]) %>%
    summarise(
      across(all_of(item_cols), mean, na.rm = TRUE),
      n_personas = n(),
      .groups = "drop"
    ) %>%
    rename(cluster = all_of(cluster_col)) %>%
    mutate(dimension = cluster_name) %>%
    select(dimension, cluster, n_personas, everything())
}

# Calculate means for all cluster dimensions
cluster_means <- map_dfr(c("seniority", "industry", "expertise", "priorities", "challenges"), 
                        calc_cluster_means)

# Convert to long format for easier analysis
cluster_means_long <- cluster_means %>%
  pivot_longer(
    cols = -c(dimension, cluster, n_personas),
    names_to = "item",
    values_to = "mean_score"
  )

cat("Cluster means calculated for", nrow(cluster_means), "unique clusters\n")
print(cluster_means_long %>% count(dimension, name = "clusters_per_dimension"))
```

# Visualizations

## Create Heatmap Function

```{r heatmap_function}
create_cluster_heatmap <- function(dim_name) {
  plot_data <- cluster_means_long %>%
    filter(dimension == dim_name) %>%
    mutate(
      cluster = str_wrap(cluster, 15),
      item = str_wrap(item, 12)
    )
  
  ggplot(plot_data, aes(x = item, y = cluster, fill = mean_score)) +
    geom_tile(color = "white", linewidth = 0.5) +
    scale_fill_gradient2(
      low = colors$secondary, mid = "white", high = colors$primary,
      midpoint = 0, name = "Mean\nUtility", 
      labels = function(x) sprintf("%.2f", x)
    ) +
    theme_minimal(base_size = 10) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
      axis.text.y = element_text(size = 9),
      plot.title = element_text(size = 12, face = "bold"),
      legend.position = "right",
      panel.grid = element_blank()
    ) +
    labs(
      title = paste(str_to_title(dim_name), "Clusters: Mean Utility Scores"),
      x = "UX Research Classes",
      y = paste(str_to_title(dim_name), "Clusters")
    )
}
```

## Generate Heatmaps for Each Dimension

```{r heatmaps, fig.height=8, fig.width=12}
# Create heatmaps for each cluster dimension
heatmap_plots <- list()
dimensions <- c("seniority", "industry", "expertise", "priorities", "challenges")

for (dim_name in dimensions) {
  heatmap_plots[[dim_name]] <- create_cluster_heatmap(dim_name)
  print(heatmap_plots[[dim_name]])
  cat("\n\n")
}
```

# Statistical Analysis

## Cluster Deviation Analysis

```{r cluster_deviations}
# Calculate deviations from overall mean for each cluster
calculate_cluster_deviations <- function() {
  # First calculate overall mean utility for each item across all clusters
  overall_item_means <- cluster_means_long %>%
    group_by(item) %>%
    summarise(
      overall_mean = mean(mean_score, na.rm = TRUE),
      .groups = "drop"
    )
  
  # Calculate deviations for each cluster
  cluster_deviations <- cluster_means_long %>%
    left_join(overall_item_means, by = "item") %>%
    mutate(
      deviation = mean_score - overall_mean,
      abs_deviation = abs(deviation)
    ) %>%
    group_by(dimension, cluster) %>%
    summarise(
      n_personas = first(n_personas),
      mean_deviation = mean(deviation, na.rm = TRUE),
      mean_abs_deviation = mean(abs_deviation, na.rm = TRUE),
      max_positive_dev = max(deviation, na.rm = TRUE),
      max_negative_dev = min(deviation, na.rm = TRUE),
      n_items = n(),
      .groups = "drop"
    ) %>%
    arrange(dimension, desc(mean_abs_deviation))
  
  return(cluster_deviations)
}

cluster_deviations <- calculate_cluster_deviations()

# Identify most extreme clusters by dimension
cat("Clusters with largest deviations from mean utility by dimension:\n\n")
for (dim in dimensions) {
  cat("**", str_to_title(dim), "Dimension:**\n")
  
  dim_deviations <- cluster_deviations %>%
    filter(dimension == dim) %>%
    arrange(desc(mean_abs_deviation))
  
  # Show top 3 most extreme clusters
  top_extreme <- dim_deviations %>%
    slice_head(n = 3) %>%
    select(cluster, n_personas, mean_deviation, mean_abs_deviation, max_positive_dev, max_negative_dev)
  
  print(top_extreme)
  cat("\n")
}

# Overall ranking of most extreme clusters across all dimensions
cat("Most extreme clusters overall (highest absolute deviation):\n")
most_extreme_overall <- cluster_deviations %>%
  arrange(desc(mean_abs_deviation)) %>%
  slice_head(n = 10) %>%
  select(dimension, cluster, n_personas, mean_deviation, mean_abs_deviation)

print(most_extreme_overall)
```

## Item-Specific Cluster Deviations

```{r item_specific_deviations}
# Detailed analysis of which items drive the largest deviations
calculate_detailed_deviations <- function() {
  # Calculate overall means by item
  overall_item_means <- cluster_means_long %>%
    group_by(item) %>%
    summarise(overall_mean = mean(mean_score, na.rm = TRUE), .groups = "drop")
  
  # Calculate deviations for each cluster-item combination
  detailed_deviations <- cluster_means_long %>%
    left_join(overall_item_means, by = "item") %>%
    mutate(
      deviation = mean_score - overall_mean,
      abs_deviation = abs(deviation)
    ) %>%
    arrange(desc(abs_deviation))
  
  return(detailed_deviations)
}

detailed_deviations <- calculate_detailed_deviations()

# Show most extreme cluster-item combinations
cat("Most extreme cluster-item deviations:\n")
extreme_combinations <- detailed_deviations %>%
  slice_head(n = 15) %>%
  select(dimension, cluster, item, mean_score, overall_mean, deviation, n_personas)

print(extreme_combinations)

# Show which items contribute most to cluster extremeness
cat("\nItems that create the most cluster differentiation:\n")
item_differentiation <- detailed_deviations %>%
  group_by(item) %>%
  summarise(
    avg_abs_deviation = mean(abs_deviation, na.rm = TRUE),
    max_deviation = max(abs_deviation, na.rm = TRUE),
    most_extreme_cluster = cluster[which.max(abs_deviation)],
    most_extreme_dimension = dimension[which.max(abs_deviation)],
    .groups = "drop"
  ) %>%
  arrange(desc(avg_abs_deviation))

print(item_differentiation)
```

## Visualization of Item-Specific Deviations

```{r item_deviation_plots, fig.height=12, fig.width=14}
# Plot 1: Most extreme cluster-item combinations
extreme_combinations_plot <- detailed_deviations %>%
  slice_head(n = 20) %>%
  mutate(
    cluster_item = paste(str_wrap(cluster, 15), str_wrap(item, 10), sep = "\n"),
    deviation_type = ifelse(deviation > 0, "Above Average", "Below Average")
  ) %>%
  ggplot(aes(x = reorder(cluster_item, abs_deviation), y = deviation, fill = deviation_type)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = paste0(dimension, "\nn=", n_personas)), 
            hjust = ifelse(detailed_deviations$deviation[1:20] > 0, -0.1, 1.1), 
            size = 2.5) +
  scale_fill_manual(values = c("Above Average" = colors$primary, 
                              "Below Average" = colors$secondary)) +
  coord_flip() +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 8),
    legend.position = "bottom"
  ) +
  labs(
    title = "Top 20 Most Extreme Cluster-Item Deviations",
    x = "Cluster - Item Combinations",
    y = "Deviation from Overall Item Mean",
    fill = "Deviation Direction",
    subtitle = "Labels show dimension and cluster size"
  )

print(extreme_combinations_plot)
cat("\n\n")

# Plot 2: Item differentiation potential
item_diff_plot <- item_differentiation %>%
  slice_head(n = 14) %>%  # All items
  mutate(
    item_wrapped = str_wrap(item, 15)
  ) %>%
  ggplot(aes(x = reorder(item_wrapped, avg_abs_deviation), y = avg_abs_deviation)) +
  geom_col(fill = colors$accent, alpha = 0.8) +
  geom_text(aes(label = paste0(most_extreme_dimension, "\n", str_wrap(most_extreme_cluster, 12))), 
            hjust = -0.1, size = 3) +
  coord_flip() +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 9)
  ) +
  labs(
    title = "Items Ranked by Cluster Differentiation Potential",
    x = "UX Research Classes",
    y = "Average Absolute Deviation Across All Clusters",
    subtitle = "Labels show dimension and cluster with maximum deviation"
  )

print(item_diff_plot)
cat("\n\n")

# Plot 3: Deviation patterns by dimension
dimension_deviation_patterns <- detailed_deviations %>%
  group_by(dimension, item) %>%
  summarise(
    avg_abs_deviation = mean(abs_deviation, na.rm = TRUE),
    max_deviation = max(abs_deviation, na.rm = TRUE),
    min_deviation = min(abs_deviation, na.rm = TRUE),
    range_deviation = max_deviation - min_deviation,
    .groups = "drop"
  )

dimension_pattern_plot <- dimension_deviation_patterns %>%
  ggplot(aes(x = str_wrap(item, 10), y = avg_abs_deviation, fill = dimension)) +
  geom_col(position = "dodge", alpha = 0.8) +
  scale_fill_viridis_d(name = "Dimension") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    legend.position = "bottom"
  ) +
  labs(
    title = "Average Item Deviation by Cluster Dimension",
    x = "UX Research Classes",
    y = "Average Absolute Deviation",
    subtitle = "Comparing how much each item varies across clusters within each dimension"
  )

print(dimension_pattern_plot)
cat("\n\n")

# Plot 4: Heatmap of extreme deviations by dimension and item
extreme_heatmap_data <- detailed_deviations %>%
  group_by(dimension, item) %>%
  slice_max(abs_deviation, n = 1) %>%  # Get most extreme cluster for each dimension-item combo
  ungroup() %>%
  select(dimension, item, cluster, deviation, abs_deviation)

extreme_heatmap <- extreme_heatmap_data %>%
  ggplot(aes(x = str_wrap(item, 10), y = dimension, fill = deviation)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = str_wrap(cluster, 12)), size = 2.5, color = "white") +
  scale_fill_gradient2(
    low = colors$secondary, mid = "white", high = colors$primary,
    midpoint = 0, name = "Max\nDeviation"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
    axis.text.y = element_text(size = 10),
    panel.grid = element_blank()
  ) +
  labs(
    title = "Most Extreme Cluster for Each Item-Dimension Combination",
    x = "UX Research Classes",
    y = "Cluster Dimensions",
    subtitle = "Cell labels show the cluster with maximum absolute deviation"
  )

print(extreme_heatmap)
```

## Visualization of Cluster Deviations

```{r deviation_plots, fig.height=10, fig.width=12}
# Create deviation plots for each dimension
create_deviation_plot <- function(dim_name) {
  plot_data <- cluster_deviations %>%
    filter(dimension == dim_name) %>%
    mutate(
      cluster_wrapped = str_wrap(cluster, 20),
      deviation_type = ifelse(mean_deviation > 0, "Above Average", "Below Average")
    )
  
  ggplot(plot_data, aes(x = reorder(cluster_wrapped, mean_abs_deviation), 
                       y = mean_deviation, fill = deviation_type)) +
    geom_col(alpha = 0.8) +
    geom_text(aes(label = paste0("n=", n_personas)), 
              hjust = ifelse(plot_data$mean_deviation > 0, -0.1, 1.1), 
              size = 3) +
    scale_fill_manual(values = c("Above Average" = colors$primary, 
                                "Below Average" = colors$secondary)) +
    coord_flip() +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 12, face = "bold"),
      legend.position = "bottom"
    ) +
    labs(
      title = paste("Cluster Deviations from Mean Utility -", str_to_title(dim_name)),
      x = "Clusters (ordered by absolute deviation)",
      y = "Mean Deviation from Overall Item Means",
      fill = "Deviation Direction"
    )
}

# Generate deviation plots
deviation_plots <- list()
for (dim_name in dimensions) {
  deviation_plots[[dim_name]] <- create_deviation_plot(dim_name)
  print(deviation_plots[[dim_name]])
  cat("\n\n")
}
```

## Cluster Utility Range Analysis

```{r utility_ranges}
# Calculate utility ranges and variability for each item across clusters
utility_analysis <- cluster_means_long %>%
  group_by(dimension, item) %>%
  summarise(
    min_utility = min(mean_score, na.rm = TRUE),
    max_utility = max(mean_score, na.rm = TRUE),
    range = max_utility - min_utility,
    mean_utility = mean(mean_score, na.rm = TRUE),
    sd_utility = sd(mean_score, na.rm = TRUE),
    cv = sd_utility / abs(mean_utility),  # Coefficient of variation
    n_clusters = n(),
    .groups = "drop"
  ) %>%
  arrange(dimension, desc(range))

# Show items with highest variability across clusters for each dimension
cat("Items with highest cluster variability by dimension:\n\n")
for (dim in dimensions) {
  cat("**", str_to_title(dim), "Dimension:**\n")
  top_var <- utility_analysis %>%
    filter(dimension == dim) %>%
    slice_max(range, n = 3) %>%
    select(item, range, mean_utility, sd_utility)
  
  print(top_var)
  cat("\n")
}
```

## Cross-Cluster Comparisons

```{r cross_cluster_comparisons}
# ANOVA-style analysis to identify items that vary most between clusters
cluster_variation_summary <- cluster_means_long %>%
  group_by(dimension, item) %>%
  summarise(
    between_cluster_var = var(mean_score, na.rm = TRUE),
    n_clusters = n(),
    overall_mean = mean(mean_score, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(dimension, desc(between_cluster_var))

# Create summary by dimension
dimension_summary <- cluster_variation_summary %>%
  group_by(dimension) %>%
  summarise(
    avg_variation = mean(between_cluster_var, na.rm = TRUE),
    max_variation = max(between_cluster_var, na.rm = TRUE),
    most_variable_item = item[which.max(between_cluster_var)],
    .groups = "drop"
  ) %>%
  arrange(desc(avg_variation))

cat("Cluster dimensions ranked by average item variability:\n")
print(dimension_summary)
```

## Item Preference Patterns

```{r preference_patterns}
# Analyze which items are consistently preferred/avoided across all clusters
item_preference_patterns <- cluster_means_long %>%
  group_by(item) %>%
  summarise(
    overall_mean = mean(mean_score, na.rm = TRUE),
    min_cluster_score = min(mean_score, na.rm = TRUE),
    max_cluster_score = max(mean_score, na.rm = TRUE),
    n_positive_clusters = sum(mean_score > 0, na.rm = TRUE),
    n_negative_clusters = sum(mean_score < 0, na.rm = TRUE),
    consistency_score = 1 - (max_cluster_score - min_cluster_score) / 2,  # Higher = more consistent
    .groups = "drop"
  ) %>%
  arrange(desc(overall_mean))

cat("Items ranked by overall preference (across all clusters):\n")
print(item_preference_patterns)

# Identify most and least consistent items
cat("\nMost consistent items (low variability across clusters):\n")
print(item_preference_patterns %>% 
       slice_max(consistency_score, n = 5) %>%
       select(item, overall_mean, consistency_score))

cat("\nMost variable items (high variability across clusters):\n")
print(item_preference_patterns %>% 
       slice_min(consistency_score, n = 5) %>%
       select(item, overall_mean, consistency_score))
```

# Cluster Profile Analysis

## Detailed Cluster Profiles

```{r cluster_profiles}
# Create detailed profiles for each cluster showing top preferences
create_cluster_profile <- function(dim_name, top_n = 3) {
  cluster_means_long %>%
    filter(dimension == dim_name) %>%
    group_by(cluster) %>%
    arrange(desc(mean_score)) %>%
    slice_head(n = top_n) %>%
    mutate(rank = row_number()) %>%
    ungroup() %>%
    select(dimension, cluster, rank, item, mean_score, n_personas)
}

# Generate profiles for each dimension
cat("Top preferences by cluster:\n\n")
for (dim in dimensions) {
  cat("##", str_to_title(dim), "Cluster Profiles\n")
  profiles <- create_cluster_profile(dim, 3)
  
  for (cluster_name in unique(profiles$cluster)) {
    cluster_data <- profiles %>% filter(cluster == cluster_name)
    cat("\n**", cluster_name, "** (n =", cluster_data$n_personas[1], "):\n")
    
    for (i in 1:nrow(cluster_data)) {
      cat(sprintf("%d. %s (%.3f)\n", 
                  cluster_data$rank[i], 
                  cluster_data$item[i], 
                  cluster_data$mean_score[i]))
    }
  }
  cat("\n\n")
}
```

## Cluster Similarity Analysis

```{r cluster_similarity}
# Calculate pairwise correlations between clusters within each dimension
calculate_cluster_correlations <- function(dim_name) {
  # Get cluster means for this dimension in wide format
  cluster_data <- cluster_means %>%
    filter(dimension == dim_name) %>%
    select(-dimension, -n_personas) %>%
    column_to_rownames("cluster")
  
  # Calculate correlation matrix
  cor_matrix <- cor(t(cluster_data), use = "complete.obs")
  
  # Convert to long format
  cor_matrix %>%
    as.data.frame() %>%
    rownames_to_column("cluster1") %>%
    pivot_longer(-cluster1, names_to = "cluster2", values_to = "correlation") %>%
    filter(cluster1 != cluster2) %>%  # Remove self-correlations
    mutate(dimension = dim_name) %>%
    arrange(desc(correlation))
}

# Calculate correlations for each dimension
cluster_correlations <- map_dfr(dimensions, calculate_cluster_correlations)

# Show most and least similar cluster pairs by dimension
cat("Most similar cluster pairs by dimension:\n\n")
for (dim in dimensions) {
  cat("**", str_to_title(dim), ":**\n")
  most_similar <- cluster_correlations %>%
    filter(dimension == dim) %>%
    slice_max(correlation, n = 2)
  
  print(most_similar %>% select(cluster1, cluster2, correlation))
  cat("\n")
}
```

## Spearman Rank Correlation Analysis

```{r spearman_rank_correlations}
# Function to calculate Spearman rank correlations for clusters within each dimension
calculate_spearman_rank_correlations <- function(dim_name) {
  # Get cluster means for this dimension
  cluster_data <- cluster_means %>%
    filter(dimension == dim_name) %>%
    select(-dimension, -n_personas)
  
  # Convert to wide format with clusters as columns
  cluster_wide <- cluster_data %>%
    pivot_longer(-cluster, names_to = "item", values_to = "mean_score") %>%
    pivot_wider(names_from = cluster, values_from = mean_score) %>%
    column_to_rownames("item")
  
  # Calculate ranks for each cluster (1 = highest utility)
  cluster_ranks <- cluster_wide %>%
    mutate(across(everything(), ~ rank(-.x, ties.method = "average")))
  
  # Calculate Spearman correlation matrix
  spearman_cor_matrix <- cor(cluster_ranks, method = "spearman", use = "complete.obs")
  
  return(list(
    ranks = cluster_ranks,
    correlations = spearman_cor_matrix,
    dimension = dim_name
  ))
}

# Calculate Spearman correlations for each dimension
spearman_results <- map(dimensions, calculate_spearman_rank_correlations)
names(spearman_results) <- dimensions

# Display correlation matrices
cat("SPEARMAN RANK CORRELATION MATRICES\n")
cat("===================================\n\n")

for (dim_name in dimensions) {
  cat("**", str_to_title(dim_name), "Dimension - Rank Correlations:**\n")
  
  # Round correlation matrix for display
  cor_matrix <- round(spearman_results[[dim_name]]$correlations, 3)
  
  # Print as formatted table
  print(cor_matrix)
  cat("\n")
  
  # Show highest and lowest correlations (excluding diagonal)
  cor_long <- cor_matrix %>%
    as.data.frame() %>%
    rownames_to_column("cluster1") %>%
    pivot_longer(-cluster1, names_to = "cluster2", values_to = "correlation") %>%
    filter(cluster1 != cluster2) %>%
    arrange(desc(correlation))
  
  cat("Highest rank correlations in", str_to_title(dim_name), ":\n")
  print(cor_long %>% slice_head(n = 3) %>% select(cluster1, cluster2, correlation))
  
  cat("\nLowest rank correlations in", str_to_title(dim_name), ":\n")
  print(cor_long %>% slice_tail(n = 3) %>% select(cluster1, cluster2, correlation))
  cat("\n\n")
}
```

## Rank-Based Heatmaps

```{r rank_heatmaps, fig.height=8, fig.width=12}
# Create rank-based heatmaps for each dimension
create_rank_heatmap <- function(dim_name) {
  # Get ranks data
  ranks_data <- spearman_results[[dim_name]]$ranks %>%
    rownames_to_column("item") %>%
    pivot_longer(-item, names_to = "cluster", values_to = "rank")
  
  # Create heatmap
  ggplot(ranks_data, aes(x = str_wrap(item, 12), y = str_wrap(cluster, 15), fill = rank)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = round(rank, 1)), size = 3, color = "white") +
    scale_fill_gradient2(
      low = colors$primary, mid = colors$accent, high = colors$secondary,
      midpoint = median(ranks_data$rank, na.rm = TRUE),
      name = "Rank\n(1=Best)", 
      guide = guide_colorbar(reverse = TRUE)
    ) +
    theme_minimal(base_size = 10) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1, size = 9),
      axis.text.y = element_text(size = 9),
      plot.title = element_text(size = 12, face = "bold"),
      legend.position = "right",
      panel.grid = element_blank()
    ) +
    labs(
      title = paste(str_to_title(dim_name), "Clusters: Item Rank Heatmap"),
      x = "UX Research Classes",
      y = paste(str_to_title(dim_name), "Clusters"),
      subtitle = "Lower numbers = higher preference ranks"
    )
}

# Generate rank heatmaps
rank_heatmap_plots <- list()
for (dim_name in dimensions) {
  rank_heatmap_plots[[dim_name]] <- create_rank_heatmap(dim_name)
  print(rank_heatmap_plots[[dim_name]])
  cat("\n\n")
}
```

## Rank Correlation Summary Analysis

```{r rank_correlation_summary}
# Summarize rank correlation patterns across dimensions
rank_correlation_summary <- map_dfr(dimensions, function(dim_name) {
  cor_matrix <- spearman_results[[dim_name]]$correlations
  
  # Convert to long format excluding diagonal
  cor_long <- cor_matrix %>%
    as.data.frame() %>%
    rownames_to_column("cluster1") %>%
    pivot_longer(-cluster1, names_to = "cluster2", values_to = "correlation") %>%
    filter(cluster1 != cluster2)
  
  # Summary statistics
  tibble(
    dimension = dim_name,
    n_clusters = nrow(cor_matrix),
    n_comparisons = nrow(cor_long),
    mean_correlation = mean(cor_long$correlation, na.rm = TRUE),
    median_correlation = median(cor_long$correlation, na.rm = TRUE),
    min_correlation = min(cor_long$correlation, na.rm = TRUE),
    max_correlation = max(cor_long$correlation, na.rm = TRUE),
    sd_correlation = sd(cor_long$correlation, na.rm = TRUE),
    most_similar_pair = paste(cor_long$cluster1[which.max(cor_long$correlation)], 
                             "vs", 
                             cor_long$cluster2[which.max(cor_long$correlation)]),
    least_similar_pair = paste(cor_long$cluster1[which.min(cor_long$correlation)], 
                              "vs", 
                              cor_long$cluster2[which.min(cor_long$correlation)])
  )
})

cat("RANK CORRELATION SUMMARY BY DIMENSION:\n")
print(rank_correlation_summary %>% 
      select(dimension, n_clusters, mean_correlation, min_correlation, max_correlation) %>%
      arrange(desc(mean_correlation)))

cat("\nDimensions with highest average rank correlations (most similar rankings):\n")
print(rank_correlation_summary %>% 
      arrange(desc(mean_correlation)) %>%
      select(dimension, mean_correlation, most_similar_pair))

cat("\nDimensions with lowest average rank correlations (most diverse rankings):\n")
print(rank_correlation_summary %>% 
      arrange(mean_correlation) %>%
      select(dimension, mean_correlation, least_similar_pair))

# Identify most consensual and most polarizing items across all clusters
consensus_analysis <- map_dfr(dimensions, function(dim_name) {
  ranks_data <- spearman_results[[dim_name]]$ranks %>%
    rownames_to_column("item")
  
  # Calculate rank variability for each item
  rank_variability <- ranks_data %>%
    pivot_longer(-item, names_to = "cluster", values_to = "rank") %>%
    group_by(item) %>%
    summarise(
      rank_sd = sd(rank, na.rm = TRUE),
      rank_range = max(rank, na.rm = TRUE) - min(rank, na.rm = TRUE),
      mean_rank = mean(rank, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(dimension = dim_name)
  
  return(rank_variability)
})

cat("\nMost consensual items (lowest rank variability across clusters):\n")
most_consensual <- consensus_analysis %>%
  group_by(item) %>%
  summarise(avg_rank_sd = mean(rank_sd, na.rm = TRUE), .groups = "drop") %>%
  arrange(avg_rank_sd) %>%
  slice_head(n = 5)
print(most_consensual)

cat("\nMost polarizing items (highest rank variability across clusters):\n")
most_polarizing <- consensus_analysis %>%
  group_by(item) %>%
  summarise(avg_rank_sd = mean(rank_sd, na.rm = TRUE), .groups = "drop") %>%
  arrange(desc(avg_rank_sd)) %>%
  slice_head(n = 5)
print(most_polarizing)
```

# Summary and Insights

## Key Findings

```{r summary_insights}
# Generate overall summary statistics
overall_stats <- list(
  n_cluster_dimensions = length(dimensions),
  n_total_clusters = nrow(cluster_means),
  n_items = length(item_cols),
  n_personas = n_distinct(llm_user_scores$user_id)
)

# Best performing clusters overall
best_clusters <- cluster_means_long %>%
  group_by(dimension, cluster) %>%
  summarise(
    avg_utility = mean(mean_score, na.rm = TRUE),
    n_personas = first(n_personas),
    .groups = "drop"
  ) %>%
  slice_max(avg_utility, n = 5) %>%
  arrange(desc(avg_utility))

# Most variable dimensions
dimension_variability <- cluster_variation_summary %>%
  group_by(dimension) %>%
  summarise(
    mean_variability = mean(between_cluster_var, na.rm = TRUE),
    total_clusters = n_distinct(cluster_means$cluster[cluster_means$dimension == dimension[1]]),
    .groups = "drop"
  ) %>%
  arrange(desc(mean_variability))

cat("ANALYSIS SUMMARY\n")
cat("================\n\n")

cat("Dataset Overview:\n")
cat("- Total cluster dimensions analyzed:", overall_stats$n_cluster_dimensions, "\n")
cat("- Total unique clusters:", overall_stats$n_total_clusters, "\n") 
cat("- Items evaluated:", overall_stats$n_items, "\n")
cat("- Personas analyzed:", overall_stats$n_personas, "\n\n")

cat("Best Performing Clusters (highest average utility):\n")
print(best_clusters)

cat("\nDimensions by Cluster Variability (most differentiated):\n")
print(dimension_variability)

cat("\nItems with Extreme Preferences:\n")
extreme_items <- item_preference_patterns %>%
  filter(abs(overall_mean) > 0.3) %>%
  arrange(desc(abs(overall_mean))) %>%
  select(item, overall_mean, min_cluster_score, max_cluster_score)

print(extreme_items)
```